---
title: "InsuranceForbes_2002"
author: "Ivan Bizberg"
date: "9/11/2020"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Insurance (Forbes 2002)



# Libraries
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)

library(performance)
library(DHARMa)
library(effects)
library(Greg)

library(lme4)
library(coxme)
library(survminer)
library(survival)
library(ordinal)
library(glmmTMB)
```

```{r}
path = "Conducta"
```

```{r}
# Create a function for censuring 
source(str_glue("C:/Users/{path}/Dropbox/PHD/Custom functions/Censoring.R"))
```

# Import data    
```{r}
Mother <- read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/RawData4.5.csv")) %>% 
  mutate(across(c(FECHFINAL1, FECHFINAL2, FECHFINAL3, ECLOSION1, ECLOSION2, ECLOSION3, ESTECLOS1, ESTECLOS2, ESTECLOS3, FECHHUEVO1, FECHHUEVO2, FECHHUEVO3), ymd)) %>%
  rename(dmESTPUESTA1_ = dmESTPUESTA1) %>% 
  rename(Clutch = PUESTA, Brood = NIDADA) %>% 
  Censoring(., 60) %>% 
  mutate(FinalDate1 = ESTECLOS1 + Time601) %>% 
  mutate(FinalDate2 = ESTECLOS2 + Time602) %>% 
  mutate(FinalDate3 = ESTECLOS3 + Time603)  
```

# Add climwin windows for this data 
```{r, include=FALSE}
ClimData = read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/ClimateVariables4.0.csv"), sep = ",", 
                    header = T,stringsAsFactors = F) %>%
  rename(Date = time) %>% mutate(Date = ymd(Date)) %>% arrange(Date) %>% 
  mutate(SST = as.numeric(SST)) %>% 
  glimpse()

# Don't run if hurry or slow pc
DATABio_Clim <- Mother %>% arrange(NIDO) %>% 
  rowwise() %>% 
  mutate(AlistChl = list(ClimData$Chl[ClimData$Date %within% interval(ESTECLOS1, FinalDate1)])) %>%
  mutate(AlistSST = list(ClimData$SST[ClimData$Date %within% interval(ESTECLOS1, FinalDate1)])) %>% 
  mutate(AlistArea_rain = list(ClimData$Area_Rain[ClimData$Date %within% interval(ESTECLOS1, FinalDate1)])) %>%
  mutate(BlistChl = list(ClimData$Chl[ClimData$Date %within% interval(ESTECLOS2, FinalDate2)])) %>%
  mutate(BlistSST = list(ClimData$SST[ClimData$Date %within% interval(ESTECLOS2, FinalDate2)])) %>% 
  mutate(BlistArea_rain = list(ClimData$Area_Rain[ClimData$Date %within% interval(ESTECLOS2, FinalDate2)])) %>%
  mutate(ClistChl = list(ClimData$Chl[ClimData$Date %within% interval(ESTECLOS3, FinalDate3)])) %>%
  mutate(ClistSST = list(ClimData$SST[ClimData$Date %within% interval(ESTECLOS3, FinalDate3)])) %>% 
  mutate(ClistArea_rain = list(ClimData$Area_Rain[ClimData$Date %within% interval(ESTECLOS3, FinalDate3)])) %>% 
      ungroup() %>% 
  mutate(
    AChl = map_dbl(AlistChl, mean, na.rm = T),
    ASST = map_dbl(AlistSST, mean, na.rm = T),
    AArea_rain = map_dbl(AlistArea_rain, mean, na.rm = T)) %>% 
  mutate(
    BChl = map_dbl(BlistChl, mean, na.rm = T),
    BSST = map_dbl(BlistSST, mean, na.rm = T),
    BArea_rain = map_dbl(BlistArea_rain, mean, na.rm = T)) %>% 
  mutate(
    CChl = map_dbl(ClistChl, mean, na.rm = T),
    CSST = map_dbl(ClistSST, mean, na.rm = T),
    CArea_rain = map_dbl(ClistArea_rain, mean, na.rm = T)) 

```

# Brood reduction increse survival probabilities specialy in marginal offspring


# Create new data for analysis BROODS OF 2
```{r}
InsuranceData <-
  Mother %>% #names() %>% sort() 
  filter(SEMANIPULO == "f") %>% 
  filter(Clutch == 2, Brood == 2) %>% 
  filter(!(DESTHUEVO2 == "e" & ESTECLOS2 <= ESTECLOS1)) %>%  #& ORDENECLOS == "f")) %>% # Remove chick B that hatched before chicks A (Probably an error at determining rank)
  filter(!ECLOSION1 > FECHFINAL1) %>% # Remove typo error
  filter(!ECLOSION2 > FECHFINAL2) %>%  # Remove typo error
  filter(!(!is.na(CONLLEGADA) & Eclos_Arrival < 21)) %>% # only use nest where laying date was after first monitoring or at least 3 weeks before arrival
  filter(!(Nest_OrderFemale > 1)) %>% # We could add male renest (n = -64)
  # filter(!(DESTHUEVO2 != "e" & FECHHUEVO2 <= ECLOSION1)) %>% # We need to remove cases when one egg deseapeared before one egg has hatch because we don;t know who is who.
  filter(!(FECHFINAL1 == FECHFINAL2 & Death601 == 1 & Death602 == 1)) %>% # We don't want chicks that died at the same date
  mutate(Sib_died2 = case_when((Death601 == 1 & FECHFINAL1 < FECHFINAL2) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(Sib_died1 = case_when((Death602 == 1 & FECHFINAL2 < FECHFINAL1) ~ 1, 
                               TRUE ~ 0)) 
```

# Edit data
```{r}
InsuranceEdit <- InsuranceData %>% 
  rename(LastSibAge2 = LastAge1, LastSibAge1 = LastAge2) %>% 
  select(c(contains(c("Sib_died")),
           ESTECLOS1, ESTECLOS2, 
           FinalDate1, FinalDate2,
           Time601, Time602,
           Death601, Death602,
           RealMotherAge, CoupleExpLocal, ANILLOHEMB,
           RealFatherAge, ANILLOMACH,
           PROPORTIONALRANK, EstHatchAsynchro12_, NIDO, WORKYEAR)) %>% 
  mutate(across(contains(c("Sib_died", "Death60", "Time", "ESTECLOS", "FinalDate")), as.character)) %>% 
  pivot_longer(all_of(ends_with(c("1", "2"))), names_to = c("col", "Status"), names_pattern = "(.*)(.)") %>%  
  pivot_wider(names_from = col) %>% # Split chick A and chick B
  mutate(Status = recode(Status, `1` = "ChickA", `2` = "ChickB")) %>% 
  mutate(across(c("FinalDate", "ESTECLOS"), ymd)) %>% glimpse 
  
```

# Add climwin windows for this data 
```{r, include=FALSE}
# Climwin data
ClimData = read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/ClimateVariables4.0.csv"), sep = ",", 
                    header = T,stringsAsFactors = F) %>%
  rename(Date = time) %>% mutate(Date = ymd(Date)) %>% arrange(Date) %>% 
  mutate(SST = as.numeric(SST)) %>% 
  group_by(Week, Year) %>% summarise(min_chl = min(Chl, na.rm = T), max_SST = max(SST, na.rm = T), 
                                     max_areaRain = max(Area_Rain, na.rm = T), min_date = min(Date)) %>% 
  arrange(Year, Week) %>% 
  mutate(across(c(min_chl, max_SST, max_areaRain), ~ifelse(abs(.) == Inf,NA,.))) %>%
  glimpse()
# Chl = 10.5 to 2 week prior quad min
# SST = 7.5 to 0 week prior quad max
# Rain area = 14 to 4 week prior quad min

# Window <- data.frame(Chl_open_window = InsuranceEdit %>% 
#                        .$LastDate - 11*7, Chl_close_window = InsuranceEdit %>% 
#                        .$LastDate - 2*7, SST_open_window = InsuranceEdit %>% 
#                        .$LastDate - 8*7, SST_close_window = InsuranceEdit %>% 
#                        .$LastDate, AreaRain_open_window = InsuranceEdit %>% 
#                        .$LastDate - 14*7, AreaRain_close_window = InsuranceEdit %>%
#                        .$LastDate - 4*7) %>% bind_cols(InsuranceEdit) %>% mutate(Week = week(LastDate))
# 
# 
# DATABio_Clim <- Window %>% arrange(LastDate, NIDO) %>% rowwise() %>% 
#   mutate(listChl = list(ClimData$min_chl[ClimData$min_date %within% interval(Chl_open_window, Chl_close_window)])) %>% 
#   mutate(listSST = list(ClimData$max_SST[ClimData$min_date %within% interval(SST_open_window, SST_close_window)])) %>% 
#   mutate(listArea_rain = list(ClimData$max_areaRain[ClimData$min_date %within% interval(AreaRain_open_window, AreaRain_close_window)])) %>% 
#       ungroup() %>% 
#   mutate(
#     Chl = map_dbl(listChl, mean, na.rm = T),
#     SST = map_dbl(listSST, mean, na.rm = T),
#     Area_rain = map_dbl(listArea_rain, mean, na.rm = T),
#          ) %>%  
#   select(-contains("list"))

# Climate experiance 
  # Add climwin windows for this data 

ClimData = read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/ClimateVariables4.0.csv"), sep = ",", 
                    header = T,stringsAsFactors = F) %>%
  rename(Date = time) %>% mutate(Date = ymd(Date)) %>% arrange(Date) %>% 
  mutate(SST = as.numeric(SST)) %>% 
  glimpse()

DATABio_Clim <- InsuranceEdit %>% arrange(NIDO) %>% 
  rowwise() %>% 
  mutate(AlistChl = list(ClimData$Chl[ClimData$Date %within% interval(ESTECLOS1, FinalDate1)])) %>%
  mutate(AlistSST = list(ClimData$SST[ClimData$Date %within% interval(ESTECLOS1, FinalDate1)])) %>% 
  mutate(AlistArea_rain = list(ClimData$Area_Rain[ClimData$Date %within% interval(ESTECLOS1, FinalDate1)])) %>%
mutate(BlistChl = list(ClimData$Chl[ClimData$Date %within% interval(ESTECLOS2, FinalDate2)])) %>%
  mutate(BlistSST = list(ClimData$SST[ClimData$Date %within% interval(ESTECLOS2, FinalDate2)])) %>% 
  mutate(BlistArea_rain = list(ClimData$Area_Rain[ClimData$Date %within% interval(ESTECLOS2, FinalDate2)])) %>%
mutate(ClistChl = list(ClimData$Chl[ClimData$Date %within% interval(ESTECLOS3, FinalDate3)])) %>%
  mutate(ClistSST = list(ClimData$SST[ClimData$Date %within% interval(ESTECLOS3, FinalDate3)])) %>% 
  mutate(ClistArea_rain = list(ClimData$Area_Rain[ClimData$Date %within% interval(ESTECLOS3, FinalDate3)])) %>% 
      ungroup() %>% 
  mutate(
    AChl = map_dbl(AlistChl, mean, na.rm = T),
    ASST = map_dbl(AlistSST, mean, na.rm = T),
    AArea_rain = map_dbl(AlistArea_rain, mean, na.rm = T)) %>% 
  mutate(
    BChl = map_dbl(BlistChl, mean, na.rm = T),
    BSST = map_dbl(BlistSST, mean, na.rm = T),
    BArea_rain = map_dbl(BlistArea_rain, mean, na.rm = T)) %>% 
  mutate(
    CChl = map_dbl(ClistChl, mean, na.rm = T),
    CSST = map_dbl(ClistSST, mean, na.rm = T),
    CArea_rain = map_dbl(ClistArea_rain, mean, na.rm = T)) 

```




# Analysis Chick B

```{r}
DfInsurance <- InsuranceEdit %>% 
  select(-contains("window"), 
         -CoupleExpLocal,
         -RealMotherAge, -ANILLOHEMB,
         -RealFatherAge, -ANILLOMACH,
         # -Chl,
         # -SST,
         # -Area_rain,
         # -Week
         ) %>% 
  # filter(!ANILLOHEMB == "SA") %>%
  drop_na() %>% 
  mutate(across(c(where(is.character), WORKYEAR, Sib_died), as.factor)) %>%
  mutate(across(c(Death60), as.character)) %>% 
  mutate(across(c(Death60, Time60), as.numeric)) %>%
  mutate(across(c(where(is.numeric), -Death60, -Time60), arm::rescale)) %>% 
  # filter((Sib_died == 1 & LastSibAge < 15) | Sib_died == 0) %>% 
  filter(Status == "ChickB") %>% 
  glimpse() # Doesn't make sense to acount sib effect on chick who allrealy survived
  #filter(Sib_died == "1") # if we want to study how age at sib death affect survival

n_B_Brood_2 <- count(DfInsurance) %>% pull
```
## Add climatique data to chicks B data 
```{r}
DATABio_Clim <- DfInsurance %>% arrange(NIDO) %>% 
  rowwise() %>% 
  mutate(listChl = list(ClimData$Chl[ClimData$Date %within% interval(ESTECLOS, FinalDate)])) %>%
  mutate(listSST = list(ClimData$SST[ClimData$Date %within% interval(ESTECLOS, FinalDate)])) %>% 
  mutate(listArea_rain = list(ClimData$Area_Rain[ClimData$Date %within% interval(ESTECLOS, FinalDate)])) %>%
      ungroup() %>% 
  mutate(
    Chl = map_dbl(listChl, mean, na.rm = T),
    SST = map_dbl(listSST, mean, na.rm = T),
    Area_rain = map_dbl(listArea_rain, mean, na.rm = T)) %>% 
  drop_na(c(Chl, SST, Area_rain)) %>% 
  mutate(across(c(Chl, SST, Area_rain),  arm::rescale))

DATABio_Clim %>% count(Sib_died)
```
Climatic variables in this analysis aren't that useful because there is no clear hypothesis behind it. For example if we thinks that parents abandon clutch when after the death of chick A death only if resources are low then is rare that if resources where rare that B chick didn't died before A. Reducing the sample size remove sib_death effect because that effect wasn't that strong and sample size is quite small now.

```{r eval=FALSE}
DATABio_Clim %<>% mutate(Sib_died = fct_relevel(Sib_died, "0", after = 1L))
levels(DATABio_Clim$Sib_died)

BestTMB = glmmTMB(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    # Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro12_ +
    # CoupleExpLocal + # No sign effect
    # RealMotherAge +  # no sign effect for B
    # I(RealMotherAge^2) +  # no sign effect for B
    # RealFatherAge +  # No sign effect
    # I(RealFatherAge^2) +  # No sign effect
    # as.numeric(WORKYEAR) +
    # Chl +
    # I(Chl^2) +
    # SST +
    # Sib_died : SST +
    # I(SST^2) +
    # Area_rain +
    # I(Area_rain^2) +
    (1|WORKYEAR), #+ (1|ANILLOHEMB), 
  family = binomial(link = "logit"),
  data = DfInsurance
)

Summary <- summary(BestTMB); Summary
DfInsurance %>% count(Sib_died)
bbmle::AICtab(BestNullB, BestTMB)
anova(BestTMB, BestNullB)
```

```{r}
BestInsB = glmer(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    # Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro12_ +
    (1|WORKYEAR), 
  family = binomial(link = "logit"),
  data = DfInsurance
)
SummaryB <- summary(BestInsB); SummaryB
```
# Plots

```{r}
plot(allEffects(BestInsB),type = "response")


ef <- effect("Sib_died", BestInsB)
x <- as.data.frame(ef)
summary(x)
ggplot(x, aes(Sib_died, fit, color=Sib_died)) + geom_point() +
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=0.4) +
  theme_bw(base_size=12)
```

# Diagnostics
```{r}
check_collinearity(BestInsB)
res = simulateResiduals(BestInsB)
plot(res)
testDispersion(res)
testUniformity(res)
testOutliers(res)
testQuantiles(res)
testZeroInflation(res)
```

```{r save B results}
FixCoef <- SummaryB %>% .$coefficients %>% 
  cbind(confint(BestInsB) %>% as.data.frame() %>% dplyr::slice(-1))

RanCoef <- SummaryB %>% .$varcor %>% as.data.frame() %>% select(-var1, -var2) %>% 
  rename(Std.Dev. = sdcor, Variance = vcov, `Random effect` = grp) %>% select(-`Random effect`)
FinalBCoef <- bind_rows(FixCoef, RanCoef) %>% rownames_to_column("Terms") 
FinalBCoef[5, "Terms"] = "Year"
write.csv(FinalBCoef, "C:/Users/Conducta/Dropbox/PHD/Git/Sibling_Insurance/CoefInsB")
```
# Analysis Chick A

```{r}
DfInsurance <- InsuranceEdit %>% 
  select(#-contains("window"),
         -CoupleExpLocal,
         # -RealMotherAge, -ANILLOHEMB,
         -RealFatherAge, -ANILLOMACH,
         # -Chl,
         # -SST,
         # -Area_rain,
         # -Week
  ) %>% 
  drop_na() %>% 
  mutate(across(c(where(is.character), WORKYEAR, Sib_died), as.factor)) %>%
  mutate(across(c(Death60), as.character)) %>% 
  mutate(across(c(Death60, Time60), as.numeric)) %>%
  mutate(across(c(where(is.numeric), -Death60, -Time60), arm::rescale)) %>% 
  filter(Status == "ChickA") %>% 
  # filter((Sib_died == 1 & LastSibAge < 50) | Sib_died == 0) %>% 
  glimpse() # Doesn't make sense to acount sib effect on chick who allrealy survived
  #filter(Sib_died == "1") # if we want to study how age at sib death affect survival
n_A_Brood_2 <- count(DfInsurance) %>% pull
```


```{r eval=FALSE}
BestTMB = glmmTMB(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    # Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro12_ +
    # CoupleExpLocal + # No sign effect
    RealMotherAge +  # sign effect for A
    I(RealMotherAge^2) +  # sign effect for A
    # RealFatherAge +  # No sign effect
    # I(RealFatherAge^2) +  # No sign effect
    # as.numeric(WORKYEAR) +
    # Chl +
    # I(Chl^2) +
    # SST +
    # SST : Sib_died +
    # I(SST^2) +
    # Area_rain +
    # I(Area_rain^2) +
    (1|WORKYEAR), #+ (1|ANILLOHEMB), 
  family = binomial(link = "logit"),
  REML = FALSE,
  ziformula = ~ 0,
  data = DfInsurance
)

Summary <- summary(BestTMB); Summary
DfInsurance %>% count(Sib_died)

bbmle::AICtab(BestNullA, BestTMB)
anova(BestTMB, BestNullA)
```


```{r save A results}
Summary
```
```{r}
BestInsA = glmer(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro12_ +
    RealMotherAge +  # sign effect for A
    I(RealMotherAge^2) + 
    (1|WORKYEAR), 
  family = binomial(link = "logit"),
  data = DfInsurance
)
SummaryA <- summary(BestInsA); SummaryA
```

```{r save results}
FixCoef <- SummaryA %>% .$coefficients %>% 
  cbind(confint(BestInsA) %>% as.data.frame() %>% dplyr::slice(-1))

RanCoef <- SummaryA %>% .$varcor %>% as.data.frame() %>% select(-var1, -var2) %>% 
  rename(Std.Dev. = sdcor, Variance = vcov, `Random effect` = grp) %>% select(-`Random effect`)
FinalBCoef <- bind_rows(FixCoef, RanCoef) %>% rownames_to_column("Terms") 
FinalBCoef[7, "Terms"] = "Year"
write.csv(FinalBCoef, "C:/Users/Conducta/Dropbox/PHD/Git/Sibling_Insurance/CoefInsA")
```
# Plots

```{r}
plot(allEffects(BestInsA),type = "response")


ef <- effect("Sib_died", BestInsA)
x <- as.data.frame(ef)
summary(x)
ggplot(x, aes(Sib_died, fit, color=Sib_died)) + geom_point() +
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=0.4) +
  theme_bw(base_size=12)
```


# Diagnostics
```{r}
check_collinearity(BestInsA)
res = simulateResiduals(BestInsA)
plot(res)
testDispersion(res)
testUniformity(res)
testOutliers(res)
testQuantiles(res)
testZeroInflation(res)
```





# Create new data for analysis BROODS OF 3
```{r}
InsuranceData3 <-
  Mother %>% #names() %>% sort() 
  filter(SEMANIPULO == "f") %>% 
  filter(Clutch == 3, Brood == 3) %>% 
  filter(DESTHUEVO3 == "e") %>% 
  filter(!(Nest_OrderFemale > 1)) %>% # We could add male renest (n = -64)
  # filter(!(DESTHUEVO2 != "e" & FECHHUEVO2 <= ECLOSION1)) %>% # We need to remove cases when one egg deseapeared before one egg has hatch because we don;t know who is who.
  filter(!((FECHFINAL1 == FECHFINAL3 & Death601 == 1 & Death603 == 1) | FECHFINAL2 == FECHFINAL3 & Death602 == 1 & Death603 == 1)) %>% 
  mutate(Sib_died1 = case_when((Death602 == 1 & FECHFINAL2 < FECHFINAL1) | (Death603 == 1 & FECHFINAL3 < FECHFINAL1) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(ASib_died2 = case_when((Death601 == 1 & FECHFINAL1 < FECHFINAL2) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(CSib_died2 = case_when((Death603 == 1 & FECHFINAL3 < FECHFINAL2) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(Sib_died3 = case_when((Death601 == 1 & FECHFINAL1 < FECHFINAL3) | (Death602 == 1 & FECHFINAL2 < FECHFINAL3) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(ASib_died3 = case_when((Death601 == 1 & FECHFINAL1 < FECHFINAL3) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(BSib_died3 = case_when((Death602 == 1 & FECHFINAL2 < FECHFINAL3) ~ 1, 
                               TRUE ~ 0))
  
InsuranceData3 %>% count(Sib_died3)
```

## Edit data Brood of 3
```{r}
InsuranceEdit3 <- InsuranceData3 %>% 
  select(c(contains(c("Sib_died", "FECHFINAL", "Death60", "Time60", "EstHatchAsynchro")), 
           # ECLOSION1, ECLOSION2, ECLOSION3,
           ANILLOHEMB, RealMotherAge,
           PROPORTIONALRANK, NIDO, WORKYEAR)) %>% 
  mutate(across(contains(c("Sib_died", "Death60", "Time", "FECHFINAL")), as.character)) %>% 
  pivot_longer(all_of(ends_with(c("1", "2", "3"))), names_to = c("col", "Status"), names_pattern = "(.*)(.)") %>%  
  pivot_wider(names_from = col) %>% # Split chick A, chick B, C
  mutate(Status = recode(Status, `1` = "ChickA", `2` = "ChickB", `3` = "ChickC")) 
  
  
InsuranceEdit3
  
```

# Analysis Chick C

```{r}
DfInsurance <- InsuranceEdit3 %>% 
  # filter(!ANILLOHEMB == "SA") %>%
  mutate(across(c(where(is.character), WORKYEAR, Sib_died), as.factor)) %>%
  mutate(across(c(Death60), as.character)) %>% 
  mutate(across(c(Death60, Time60), as.numeric)) %>%
  mutate(across(c(where(is.numeric), -Death60, -Time60), arm::rescale)) %>% 
  # filter((Sib_died == 1 & LastSibAge < 15) | Sib_died == 0) %>% 
  filter(Status == "ChickC") %>% 
  select(Sib_died, Death60, EstHatchAsynchro23_, PROPORTIONALRANK, WORKYEAR,
         ASib_died, BSib_died, # Correct?
         RealMotherAge, ANILLOHEMB) %>% 
  drop_na() %>% 
  glimpse() # Doesn't make sense to acount sib effect on chick who allrealy survived
  #filter(Sib_died == "1") # if we want to study how age at sib death affect survival

n_C_Brood_3 <- count(DfInsurance) %>% pull
```


```{r eval=FALSE}
BestTMB = glmmTMB(
  Death60 ~  #Sib_died + 
    ASib_died + BSib_died + # No sign effect
    PROPORTIONALRANK +
    EstHatchAsynchro23_ +
    # CoupleExpLocal + # No sign effect
    RealMotherAge +  # sign effect for C
    I(RealMotherAge^2) +  # sign effect for C
    # RealFatherAge +  # No sign effect
    # I(RealFatherAge^2) +  # No sign effect
    # as.numeric(WORKYEAR) +
    # Chl +
    # I(Chl^2) +
    # SST +
    # SST : Sib_died +
    # I(SST^2) +
    # Area_rain +
    # I(Area_rain^2) +
    (1|WORKYEAR) + (1|ANILLOHEMB), 
  family = binomial(link = "logit"),
  data = DfInsurance
)

Summary <- summary(BestTMB); Summary
DfInsurance %>% count(Sib_died)
bbmle::AICtab(BestNullB, BestTMB)
anova(BestTMB, BestNullB)
```

```{r}
BestInsB = glmer(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    # Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro23_ +
    (1|WORKYEAR), 
  family = binomial(link = "logit"),
  data = DfInsurance
)
SummaryB <- summary(BestInsB); SummaryB
```
# Plots

```{r}
plot(allEffects(BestInsB),type = "response")


ef <- effect("Sib_died", BestInsB)
x <- as.data.frame(ef)
summary(x)
ggplot(x, aes(Sib_died, fit, color=Sib_died)) + geom_point() +
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=0.4) +
  theme_bw(base_size=12)
```

# Diagnostics
```{r}
check_collinearity(BestInsB)
res = simulateResiduals(BestInsB)
plot(res)
testDispersion(res)
testUniformity(res)
testOutliers(res)
testQuantiles(res)
testZeroInflation(res)
```

```{r save B results}
FixCoef <- SummaryB %>% .$coefficients %>% 
  cbind(confint(BestInsB) %>% as.data.frame() %>% dplyr::slice(-1))

RanCoef <- SummaryB %>% .$varcor %>% as.data.frame() %>% select(-var1, -var2) %>% 
  rename(Std.Dev. = sdcor, Variance = vcov, `Random effect` = grp) %>% select(-`Random effect`)
FinalBCoef <- bind_rows(FixCoef, RanCoef) %>% rownames_to_column("Terms") 
FinalBCoef[5, "Terms"] = "Year"
write.csv(FinalBCoef, "C:/Users/Conducta/Dropbox/PHD/Git/Sibling_Insurance/CoefInsB")
```
# Analysis Chick A from broods of 3

```{r}
DfInsurance <- InsuranceEdit3 %>% 
  mutate(across(c(where(is.character), WORKYEAR, Sib_died), as.factor)) %>%
  mutate(across(c(Death60), as.character)) %>% 
  mutate(across(c(Death60, Time60), as.numeric)) %>%
  mutate(across(c(where(is.numeric), -Death60, -Time60), arm::rescale)) %>% 
  filter(Status == "ChickA") %>% 
  select(PROPORTIONALRANK, EstHatchAsynchro12_, Sib_died, Death60, Status, WORKYEAR,
         RealMotherAge, ANILLOHEMB) %>% 
  drop_na() %>% 
  # filter((Sib_died == 1 & LastSibAge < 50) | Sib_died == 0) %>% 
  glimpse() # Doesn't make sense to acount sib effect on chick who allrealy survived
  #filter(Sib_died == "1") # if we want to study how age at sib death affect survival

DfInsurance %>% count(Sib_died)
n_A_Brood_3 <- count(DfInsurance) %>% pull
```


```{r eval=FALSE}
BestTMB = glmmTMB(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    # Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro12_ +
    # CoupleExpLocal + # No sign effect
    RealMotherAge +  # sign effect for A
    I(RealMotherAge^2) +  # sign effect for A
    # RealFatherAge +  # No sign effect
    # I(RealFatherAge^2) +  # No sign effect
    # as.numeric(WORKYEAR) +
    # Chl +
    # I(Chl^2) +
    # SST +
    # SST : Sib_died +
    # I(SST^2) +
    # Area_rain +
    # I(Area_rain^2) +
    (1|WORKYEAR),# + (1|ANILLOHEMB), 
  family = binomial(link = "logit"),
  REML = FALSE,
  ziformula = ~ 0,
  data = DfInsurance
)

Summary <- summary(BestTMB); Summary
DfInsurance %>% count(Sib_died)

bbmle::AICtab(BestNullA, BestTMB)
anova(BestTMB, BestNullA)
```


```{r save A results}
Summary
```
```{r}
BestInsA = glmer(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro12_ +
    RealMotherAge +  # sign effect for A
    I(RealMotherAge^2) + 
    (1|WORKYEAR), 
  family = binomial(link = "logit"),
  data = DfInsurance
)
SummaryA <- summary(BestInsA); SummaryA
```

```{r save results}
FixCoef <- SummaryA %>% .$coefficients %>% 
  cbind(confint(BestInsA) %>% as.data.frame() %>% dplyr::slice(-1))

RanCoef <- SummaryA %>% .$varcor %>% as.data.frame() %>% select(-var1, -var2) %>% 
  rename(Std.Dev. = sdcor, Variance = vcov, `Random effect` = grp) %>% select(-`Random effect`)
FinalBCoef <- bind_rows(FixCoef, RanCoef) %>% rownames_to_column("Terms") 
FinalBCoef[7, "Terms"] = "Year"
write.csv(FinalBCoef, "C:/Users/Conducta/Dropbox/PHD/Git/Sibling_Insurance/CoefInsA")
```
# Plots

```{r}
plot(allEffects(BestInsA),type = "response")


ef <- effect("Sib_died", BestInsA)
x <- as.data.frame(ef)
summary(x)
ggplot(x, aes(Sib_died, fit, color=Sib_died)) + geom_point() +
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=0.4) +
  theme_bw(base_size=12)
```


# Diagnostics
```{r}
check_collinearity(BestInsA)
res = simulateResiduals(BestInsA)
plot(res)
testDispersion(res)
testUniformity(res)
testOutliers(res)
testQuantiles(res)
testZeroInflation(res)
```


# Analysis Chick B from broods of 3

```{r}
DfInsurance <- InsuranceEdit3 %>% 
  mutate(across(c(where(is.character), WORKYEAR, Sib_died), as.factor)) %>%
  mutate(across(c(Death60), as.character)) %>% 
  mutate(across(c(Death60, Time60), as.numeric)) %>%
  mutate(across(c(where(is.numeric), -Death60, -Time60), arm::rescale)) %>% 
  filter(Status == "ChickB") %>% 
  select(PROPORTIONALRANK, EstHatchAsynchro12_, ASib_died, CSib_died, Death60, Status, WORKYEAR,
         RealMotherAge, ANILLOHEMB) %>% 
  drop_na() %>% 
  # filter((Sib_died == 1 & LastSibAge < 50) | Sib_died == 0) %>% 
  glimpse() # Doesn't make sense to acount sib effect on chick who allrealy survived
  #filter(Sib_died == "1") # if we want to study how age at sib death affect survival

DfInsurance %>% count(Sib_died)
n_B_Brood_3 <- count(DfInsurance) %>% pull
```


```{r eval=FALSE}
BestTMB = glmmTMB(
  Death60 ~  OldSib_died + YoungSib_died +
    # OldSib_died : YoungSib_died + # No sign effect
    PROPORTIONALRANK +
    # Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro12_ +
    # CoupleExpLocal + # No sign effect
    RealMotherAge +  # sign effect for A
    I(RealMotherAge^2) +  # sign effect for A
    # RealFatherAge +  # No sign effect
    # I(RealFatherAge^2) +  # No sign effect
    # as.numeric(WORKYEAR) +
    # Chl +
    # I(Chl^2) +
    # SST +
    # SST : Sib_died +
    # I(SST^2) +
    # Area_rain +
    # I(Area_rain^2) +
    (1|WORKYEAR),# + (1|ANILLOHEMB), 
  family = binomial(link = "logit"),
  REML = FALSE,
  ziformula = ~ 0,
  data = DfInsurance
)

performance::check_collinearity(BestTMB)
Summary <- summary(BestTMB); Summary
DfInsurance %>% count(Sib_died)

bbmle::AICtab(BestNullA, BestTMB)
anova(BestTMB, BestNullA)
```

### Sample size data frame 
```{r}
Sample_size <- data.frame(
  Analysis = c("n_A_Brood_2", "n_B_Brood_2", "n_A_Brood_3", "n_B_Brood_3", "n_C_Brood_3"),
  Sample_size = c(n_A_Brood_2, n_B_Brood_2, n_A_Brood_3, n_B_Brood_3, n_C_Brood_3)) %>% 
  mutate(Brood = str_sub(Analysis, -1))
write_csv(Sample_size, "SampleSize.csv")
```
