---
title: "InsuranceForbes_2002"
author: "Ivan Bizberg"
date: "9/11/2020"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Insurance (Forbes 2002)



# Libraries
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)

library(performance)
library(DHARMa)
library(effects)
library(Greg)

library(lme4)
library(coxme)
library(survminer)
library(survival)
library(ordinal)
library(glmmTMB)
```

```{r}
path = "Conducta"
```

# Import data    
```{r}
Mother <- read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/RawData4.5.csv")) %>% 
  mutate(across(c(FECHFINAL1, FECHFINAL2, FECHFINAL3, ECLOSION1, ECLOSION2, ECLOSION3, ESTECLOS1, ESTECLOS2, ESTECLOS3, FECHHUEVO1, FECHHUEVO2, FECHHUEVO3), ymd)) %>% 
  rename(dmESTPUESTA1_ = dmESTPUESTA1) %>% 
  rename(Clutch = PUESTA, Brood = NIDADA)
```

# Brood reduction increse survival probabilities specialy in marginal offspring
```{r}
# Create a function for censuring 
Censoring <- function(data, x){
  usethis::ui_done("function that censure the last age and death")
  data %>% mutate(Death601 = case_when(MURIO1 == "f" & LastAge1 >= x ~ 0, # Right censoring
                                          MURIO1 == "t" & LastAge1 < x ~ 1,
                                          MURIO1 == "t" & LastAge1 >= x ~ 0,
                                          MURIO1 == "f" & LastAge1 < x ~ NA_real_,
                                          TRUE ~ NA_real_)) %>%  
    mutate(Death602 = case_when(MURIO2 == "f" & LastAge2 >= x ~ 0,
                                   MURIO2 == "t" & LastAge2 < x ~ 1,
                                   MURIO2 == "t" & LastAge2 >= x ~ 0,
                                   MURIO2 == "f" & LastAge2 < x ~ NA_real_,
                                   TRUE ~ NA_real_)) %>% 
    mutate(Death603 = case_when(MURIO3 == "f" & LastAge3 >= x ~ 0,
                                   MURIO3 == "t" & LastAge3 < x ~ 1,
                                   MURIO3 == "t" & LastAge3 >= x ~ 0,
                                   MURIO3 == "f" & LastAge3 < x ~ NA_real_,
                                   TRUE ~ NA_real_)) %>% 
    mutate(Time601 = case_when(Death601 == 0 ~ x,
                               Death601 == 1 ~ as.numeric(LastAge1))) %>% 
    mutate(Time602 = case_when(Death602 == 0 ~ x,
                               Death602 == 1 ~ as.numeric(LastAge2))) %>% 
    mutate(Time603 = case_when(Death603 == 0 ~ x,
                               Death603 == 1 ~ as.numeric(LastAge3)))
}
```


# Create new data for analysis BROODS OF 2
```{r}
InsuranceData <-
  Mother %>% #names() %>% sort() 
  filter(SEMANIPULO == "f") %>% 
  filter(Clutch == 2, Brood == 2) %>% 
  filter(!(DESTHUEVO2 == "e" & ESTECLOS2 <= ESTECLOS1)) %>%  #& ORDENECLOS == "f")) %>% # Remove chick B that hatched before chicks A (Probably an error at determining rank)
  filter(!ECLOSION1 > FECHFINAL1) %>% # Remove typo error
  filter(!ECLOSION2 > FECHFINAL2) %>%  # Remove typo error
  filter(!(!is.na(CONLLEGADA) & Eclos_Arrival < 21)) %>% # only use nest where laying date was after first monitoring or at least 3 weeks before arrival
  filter(!(Nest_OrderFemale > 1)) %>% # We could add male renest (n = -64)
  # filter(!(DESTHUEVO2 != "e" & FECHHUEVO2 <= ECLOSION1)) %>% # We need to remove cases when one egg deseapeared before one egg has hatch because we don;t know who is who.
  Censoring(., 60) %>% # function
  mutate(LastDate1 = ECLOSION1 + Time601) %>% 
  mutate(LastDate2 = ECLOSION2 + Time602) %>% 
  filter(!(FECHFINAL1 == FECHFINAL2 & Death601 == 1 & Death602 == 1)) %>% # We don't want chicks that died at the same date
  mutate(Sib_died2 = case_when((Death601 == 1 & FECHFINAL1 < FECHFINAL2) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(Sib_died1 = case_when((Death602 == 1 & FECHFINAL2 < FECHFINAL1) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(AgeatSibDeath1 = as.numeric(FECHFINAL2 - ECLOSION1)) %>% # Age of A when B died 
  mutate(AgeatSibDeath2 = as.numeric(FECHFINAL1 - ECLOSION2)) # Age of B when A died

InsuranceEdit <- InsuranceData %>% 
  rename(LastSibAge2 = LastAge1, LastSibAge1 = LastAge2) %>% 
  select(c(contains(c("Sib_died", "LastDate")), 
           # ECLOSION1, ECLOSION2,
           Time601, Time602,
           Death601, Death602,
           RealMotherAge, CoupleExpLocal, ANILLOHEMB,
           RealFatherAge, ANILLOMACH,
           PROPORTIONALRANK, EstHatchAsynchro12_, NIDO, WORKYEAR)) %>% 
  mutate(across(contains(c("Sib_died", "LastDate", "Death60", "Time")), as.character)) %>% 
  pivot_longer(all_of(ends_with(c("1", "2"))), names_to = c("col", "Status"), names_pattern = "(.*)(.)") %>%  
  pivot_wider(names_from = col) %>% # Split chick A and chick B
  mutate(Status = recode(Status, `1` = "ChickA", `2` = "ChickB")) %>% 
  mutate(LastDate = ymd(LastDate))  
  
```

# Add climwin windows for this data 
```{r, include=FALSE}

ClimData = read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/ClimateVariables4.0.csv"), sep = ",", 
                    header = T,stringsAsFactors = F) %>%
  rename(Date = time) %>% mutate(Date = ymd(Date)) %>% arrange(Date) %>% 
  mutate(SST = as.numeric(SST)) %>% 
  group_by(Week, Year) %>% summarise(min_chl = min(Chl, na.rm = T), max_SST = max(SST, na.rm = T), 
                                     max_areaRain = max(Area_Rain, na.rm = T), min_date = min(Date)) %>% 
  arrange(Year, Week) %>% 
  mutate(across(c(min_chl, max_SST, max_areaRain), ~ifelse(abs(.) == Inf,NA,.))) %>%
  glimpse()
# Chl = 10.5 to 2 week prior quad min
# SST = 7.5 to 0 week prior quad max
# Rain area = 14 to 4 week prior quad min

Window <- data.frame(Chl_open_window = InsuranceEdit %>% 
                       .$LastDate - 11*7, Chl_close_window = InsuranceEdit %>% 
                       .$LastDate - 2*7, SST_open_window = InsuranceEdit %>% 
                       .$LastDate - 8*7, SST_close_window = InsuranceEdit %>% 
                       .$LastDate, AreaRain_open_window = InsuranceEdit %>% 
                       .$LastDate - 14*7, AreaRain_close_window = InsuranceEdit %>%
                       .$LastDate - 4*7) %>% bind_cols(InsuranceEdit) %>% mutate(Week = week(LastDate))


DATABio_Clim <- Window %>% arrange(LastDate, NIDO) %>% rowwise() %>% 
  mutate(listChl = list(ClimData$min_chl[ClimData$min_date %within% interval(Chl_open_window, Chl_close_window)])) %>% 
  mutate(listSST = list(ClimData$max_SST[ClimData$min_date %within% interval(SST_open_window, SST_close_window)])) %>% 
  mutate(listArea_rain = list(ClimData$max_areaRain[ClimData$min_date %within% interval(AreaRain_open_window, AreaRain_close_window)])) %>% 
      ungroup() %>% 
  mutate(
    Chl = map_dbl(listChl, mean, na.rm = T),
    SST = map_dbl(listSST, mean, na.rm = T),
    Area_rain = map_dbl(listArea_rain, mean, na.rm = T),
         ) %>%  
  select(-contains("list"))
  

```




# Analysis Chick B

```{r}
DfInsurance <- InsuranceEdit %>% 
  select(-contains("window"), 
         -CoupleExpLocal,
         -RealMotherAge,
         -ANILLOHEMB,
         -RealFatherAge, -ANILLOMACH,
         # -Chl,
         # -SST,
         # -Area_rain,
         # -Week
         ) %>% 
  # filter(!ANILLOHEMB == "SA") %>%
  drop_na() %>% 
  mutate(across(c(where(is.character), WORKYEAR, Sib_died), as.factor)) %>%
  mutate(across(c(Death60), as.character)) %>% 
  mutate(across(c(Death60, Time60), as.numeric)) %>%
  mutate(across(c(where(is.numeric), -Death60, -Time60), arm::rescale)) %>% 
  # filter((Sib_died == 1 & LastSibAge < 15) | Sib_died == 0) %>% 
  filter(Status == "ChickB") %>% 
  glimpse() # Doesn't make sense to acount sib effect on chick who allrealy survived
  #filter(Sib_died == "1") # if we want to study how age at sib death affect survival
```


```{r eval=FALSE}
BestTMB = glmmTMB(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    # Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro12_ +
    # CoupleExpLocal + # No sign effect
    # RealMotherAge +  # sign effect for A
    # I(RealMotherAge^2) +  # sign effect for A
    # RealFatherAge +  # No sign effect
    # I(RealFatherAge^2) +  # No sign effect
    # as.numeric(WORKYEAR) +
    # Chl +
    # I(Chl^2) +
    # SST +
    # SST : Sib_died +
    # I(SST^2) +
    # Area_rain +
    # I(Area_rain^2) +
    (1|WORKYEAR), #+ (1|ANILLOHEMB), 
  family = binomial(link = "logit"),
  data = DfInsurance
)

Summary <- summary(BestTMB); Summary
DfInsurance %>% count(Sib_died)
bbmle::AICtab(BestNullB, BestTMB)
anova(BestTMB, BestNullB)
```

```{r}
BestInsB = glmer(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    # Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro12_ +
    (1|WORKYEAR), 
  family = binomial(link = "logit"),
  data = DfInsurance
)
SummaryB <- summary(BestInsB); SummaryB
```
# Plots

```{r}
plot(allEffects(BestInsB),type = "response")


ef <- effect("Sib_died", BestInsB)
x <- as.data.frame(ef)
summary(x)
ggplot(x, aes(Sib_died, fit, color=Sib_died)) + geom_point() +
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=0.4) +
  theme_bw(base_size=12)
```

# Diagnostics
```{r}
check_collinearity(BestInsB)
res = simulateResiduals(BestInsB)
plot(res)
testDispersion(res)
testUniformity(res)
testOutliers(res)
testQuantiles(res)
testZeroInflation(res)
```

```{r save B results}
FixCoef <- SummaryB %>% .$coefficients %>% 
  cbind(confint(BestInsB) %>% as.data.frame() %>% dplyr::slice(-1))

RanCoef <- SummaryB %>% .$varcor %>% as.data.frame() %>% select(-var1, -var2) %>% 
  rename(Std.Dev. = sdcor, Variance = vcov, `Random effect` = grp) %>% select(-`Random effect`)
FinalBCoef <- bind_rows(FixCoef, RanCoef) %>% rownames_to_column("Terms") 
FinalBCoef[5, "Terms"] = "Year"
write.csv(FinalBCoef, "C:/Users/Conducta/Dropbox/PHD/Git/Sibling_Insurance/CoefInsB")
```
# Analysis Chick A

```{r}
DfInsurance <- DATABio_Clim %>% 
  select(-contains("window"), 
         -CoupleExpLocal,
         # -RealMotherAge, -ANILLOHEMB,
         -RealFatherAge, -ANILLOMACH,
         -Chl,
         -SST,
         -Area_rain,
         -Week) %>% 
  drop_na() %>% 
  mutate(across(c(where(is.character), WORKYEAR, Sib_died), as.factor)) %>%
  mutate(across(c(AgeatSibDeath, LastSibAge, Death60), as.character)) %>% 
  mutate(across(c(AgeatSibDeath, LastSibAge, Death60, Time60), as.numeric)) %>%
  mutate(across(c(where(is.numeric), -Death60, -AgeatSibDeath, -LastSibAge, -Time60), arm::rescale)) %>% 
  filter(Status == "ChickA") %>% 
  # filter((Sib_died == 1 & LastSibAge < 50) | Sib_died == 0) %>% 
  glimpse() # Doesn't make sense to acount sib effect on chick who allrealy survived
  #filter(Sib_died == "1") # if we want to study how age at sib death affect survival
```


```{r eval=FALSE}
BestTMB = glmmTMB(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro12_ +
    # CoupleExpLocal + # No sign effect
    RealMotherAge +  # sign effect for A
    I(RealMotherAge^2) +  # sign effect for A
    # RealFatherAge +  # No sign effect
    # I(RealFatherAge^2) +  # No sign effect
    # as.numeric(WORKYEAR) +
    # Chl +
    # I(Chl^2) +
    # SST +
    # SST : Sib_died +
    # I(SST^2) +
    # Area_rain +
    # I(Area_rain^2) +
    (1|WORKYEAR) + (1|ANILLOHEMB), 
  family = binomial(link = "logit"),
  REML = FALSE,
  ziformula = ~ 0,
  data = DfInsurance
)

Summary <- summary(BestTMB); Summary
DfInsurance %>% count(Sib_died)

bbmle::AICtab(BestNullA, BestTMB)
anova(BestTMB, BestNullA)
```


```{r save A results}
Summary
```
```{r}
BestInsA = glmer(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro12_ +
    RealMotherAge +  # sign effect for A
    I(RealMotherAge^2) + 
    (1|WORKYEAR), 
  family = binomial(link = "logit"),
  data = DfInsurance
)
SummaryA <- summary(BestInsA); SummaryA
```

```{r save results}
FixCoef <- SummaryA %>% .$coefficients %>% 
  cbind(confint(BestInsA) %>% as.data.frame() %>% dplyr::slice(-1))

RanCoef <- SummaryA %>% .$varcor %>% as.data.frame() %>% select(-var1, -var2) %>% 
  rename(Std.Dev. = sdcor, Variance = vcov, `Random effect` = grp) %>% select(-`Random effect`)
FinalBCoef <- bind_rows(FixCoef, RanCoef) %>% rownames_to_column("Terms") 
FinalBCoef[7, "Terms"] = "Year"
write.csv(FinalBCoef, "C:/Users/Conducta/Dropbox/PHD/Git/Sibling_Insurance/CoefInsA")
```
# Plots

```{r}
plot(allEffects(BestInsA),type = "response")


ef <- effect("Sib_died", BestInsA)
x <- as.data.frame(ef)
summary(x)
ggplot(x, aes(Sib_died, fit, color=Sib_died)) + geom_point() +
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=0.4) +
  theme_bw(base_size=12)
```


# Diagnostics
```{r}
check_collinearity(BestInsA)
res = simulateResiduals(BestInsA)
plot(res)
testDispersion(res)
testUniformity(res)
testOutliers(res)
testQuantiles(res)
testZeroInflation(res)
```





# Create new data for analysis BROODS OF 3
```{r}
InsuranceData3 <-
  Mother %>% #names() %>% sort() 
  filter(SEMANIPULO == "f") %>% 
  filter(Clutch == 3, Brood == 3) %>% 
  filter(DESTHUEVO3 == "e") %>% 
  filter(!(Nest_OrderFemale > 1)) %>% # We could add male renest (n = -64)
  # filter(!(DESTHUEVO2 != "e" & FECHHUEVO2 <= ECLOSION1)) %>% # We need to remove cases when one egg deseapeared before one egg has hatch because we don;t know who is who.
  Censoring(., 60) %>% # function
  mutate(LastDate1 = ECLOSION1 + Time601) %>% 
  mutate(LastDate2 = ECLOSION2 + Time602) %>% 
  mutate(LastDate3 = ECLOSION3 + Time603) %>% 
  filter(!((FECHFINAL1 == FECHFINAL3 & Death601 == 1 & Death603 == 1) | FECHFINAL2 == FECHFINAL3 & Death602 == 1 & Death603 == 1)) %>% 
  mutate(Sib_died1 = case_when((Death602 == 1 & FECHFINAL2 < FECHFINAL1) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(Sib_died2 = case_when((Death601 == 1 & FECHFINAL1 < FECHFINAL2) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(Sib_died3 = case_when((Death601 == 1 & FECHFINAL1 < FECHFINAL3) | (Death602 == 1 & FECHFINAL2 < FECHFINAL3) ~ 1, 
                               TRUE ~ 0))
  
InsuranceData3 %>% count(Sib_died2)

InsuranceEdit3 <- InsuranceData3 %>% 
  rename(LastSibAge2 = LastAge1, LastSibAge1 = LastAge2) %>% 
  select(c(contains(c("Sib_died", "FECHFINAL", "Death60", "Time60", "LastDate")), 
           # ECLOSION1, ECLOSION2, ECLOSION3,
           PROPORTIONALRANK, EstHatchAsynchro23_, NIDO, WORKYEAR)) %>% 
  mutate(across(contains(c("Sib_died", "LastDate", "Death60", "Time", "FECHFINAL")), as.character)) %>% 
  pivot_longer(all_of(ends_with(c("1", "2", "3"))), names_to = c("col", "Status"), names_pattern = "(.*)(.)") %>%  
  pivot_wider(names_from = col) %>% # Split chick A and chick B
  mutate(Status = recode(Status, `1` = "ChickA", `2` = "ChickB", `3` = "ChickC")) %>% 
  mutate(LastDate = ymd(LastDate))  
  
  
InsuranceEdit3
  
```

# Analysis Chick B

```{r}
DfInsurance <- InsuranceEdit3 %>% 
  select(-contains("window"), 
         # -CoupleExpLocal,
         # -RealMotherAge,
         # -ANILLOHEMB,
         # -RealFatherAge, -ANILLOMACH,
         # -Chl,
         # -SST,
         # -Area_rain,
         # -Week
         ) %>% 
  # filter(!ANILLOHEMB == "SA") %>%
  drop_na() %>% 
  mutate(across(c(where(is.character), WORKYEAR, Sib_died), as.factor)) %>%
  mutate(across(c(Death60), as.character)) %>% 
  mutate(across(c(Death60, Time60), as.numeric)) %>%
  mutate(across(c(where(is.numeric), -Death60, -Time60), arm::rescale)) %>% 
  # filter((Sib_died == 1 & LastSibAge < 15) | Sib_died == 0) %>% 
  filter(Status == "ChickC") %>% 
  glimpse() # Doesn't make sense to acount sib effect on chick who allrealy survived
  #filter(Sib_died == "1") # if we want to study how age at sib death affect survival
```


```{r eval=FALSE}
BestTMB = glmmTMB(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    Sib_died +
    EstHatchAsynchro23_ +
    # CoupleExpLocal + # No sign effect
    # RealMotherAge +  # sign effect for A
    # I(RealMotherAge^2) +  # sign effect for A
    # RealFatherAge +  # No sign effect
    # I(RealFatherAge^2) +  # No sign effect
    # as.numeric(WORKYEAR) +
    # Chl +
    # I(Chl^2) +
    # SST +
    # SST : Sib_died +
    # I(SST^2) +
    # Area_rain +
    # I(Area_rain^2) +
    (1|WORKYEAR), #+ (1|ANILLOHEMB), 
  family = binomial(link = "logit"),
  data = DfInsurance
)

Summary <- summary(BestTMB); Summary
DfInsurance %>% count(Sib_died)
bbmle::AICtab(BestNullB, BestTMB)
anova(BestTMB, BestNullB)
```

```{r}
BestInsB = glmer(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    # Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro23_ +
    (1|WORKYEAR), 
  family = binomial(link = "logit"),
  data = DfInsurance
)
SummaryB <- summary(BestInsB); SummaryB
```
# Plots

```{r}
plot(allEffects(BestInsB),type = "response")


ef <- effect("Sib_died", BestInsB)
x <- as.data.frame(ef)
summary(x)
ggplot(x, aes(Sib_died, fit, color=Sib_died)) + geom_point() +
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=0.4) +
  theme_bw(base_size=12)
```

# Diagnostics
```{r}
check_collinearity(BestInsB)
res = simulateResiduals(BestInsB)
plot(res)
testDispersion(res)
testUniformity(res)
testOutliers(res)
testQuantiles(res)
testZeroInflation(res)
```

```{r save B results}
FixCoef <- SummaryB %>% .$coefficients %>% 
  cbind(confint(BestInsB) %>% as.data.frame() %>% dplyr::slice(-1))

RanCoef <- SummaryB %>% .$varcor %>% as.data.frame() %>% select(-var1, -var2) %>% 
  rename(Std.Dev. = sdcor, Variance = vcov, `Random effect` = grp) %>% select(-`Random effect`)
FinalBCoef <- bind_rows(FixCoef, RanCoef) %>% rownames_to_column("Terms") 
FinalBCoef[5, "Terms"] = "Year"
write.csv(FinalBCoef, "C:/Users/Conducta/Dropbox/PHD/Git/Sibling_Insurance/CoefInsB")
```
# Analysis Chick A

```{r}
DfInsurance <- DATABio_Clim %>% 
  select(-contains("window"), 
         -CoupleExpLocal,
         # -RealMotherAge, -ANILLOHEMB,
         -RealFatherAge, -ANILLOMACH,
         -Chl,
         -SST,
         -Area_rain,
         -Week) %>% 
  drop_na() %>% 
  mutate(across(c(where(is.character), WORKYEAR, Sib_died), as.factor)) %>%
  mutate(across(c(AgeatSibDeath, LastSibAge, Death60), as.character)) %>% 
  mutate(across(c(AgeatSibDeath, LastSibAge, Death60, Time60), as.numeric)) %>%
  mutate(across(c(where(is.numeric), -Death60, -AgeatSibDeath, -LastSibAge, -Time60), arm::rescale)) %>% 
  filter(Status == "ChickA") %>% 
  # filter((Sib_died == 1 & LastSibAge < 50) | Sib_died == 0) %>% 
  glimpse() # Doesn't make sense to acount sib effect on chick who allrealy survived
  #filter(Sib_died == "1") # if we want to study how age at sib death affect survival
```


```{r eval=FALSE}
BestTMB = glmmTMB(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro12_ +
    # CoupleExpLocal + # No sign effect
    RealMotherAge +  # sign effect for A
    I(RealMotherAge^2) +  # sign effect for A
    # RealFatherAge +  # No sign effect
    # I(RealFatherAge^2) +  # No sign effect
    # as.numeric(WORKYEAR) +
    # Chl +
    # I(Chl^2) +
    # SST +
    # SST : Sib_died +
    # I(SST^2) +
    # Area_rain +
    # I(Area_rain^2) +
    (1|WORKYEAR) + (1|ANILLOHEMB), 
  family = binomial(link = "logit"),
  REML = FALSE,
  ziformula = ~ 0,
  data = DfInsurance
)

Summary <- summary(BestTMB); Summary
DfInsurance %>% count(Sib_died)

bbmle::AICtab(BestNullA, BestTMB)
anova(BestTMB, BestNullA)
```


```{r save A results}
Summary
```
```{r}
BestInsA = glmer(
  Death60 ~  Sib_died + 
    PROPORTIONALRANK +
    Sib_died : PROPORTIONALRANK +
    EstHatchAsynchro12_ +
    RealMotherAge +  # sign effect for A
    I(RealMotherAge^2) + 
    (1|WORKYEAR), 
  family = binomial(link = "logit"),
  data = DfInsurance
)
SummaryA <- summary(BestInsA); SummaryA
```

```{r save results}
FixCoef <- SummaryA %>% .$coefficients %>% 
  cbind(confint(BestInsA) %>% as.data.frame() %>% dplyr::slice(-1))

RanCoef <- SummaryA %>% .$varcor %>% as.data.frame() %>% select(-var1, -var2) %>% 
  rename(Std.Dev. = sdcor, Variance = vcov, `Random effect` = grp) %>% select(-`Random effect`)
FinalBCoef <- bind_rows(FixCoef, RanCoef) %>% rownames_to_column("Terms") 
FinalBCoef[7, "Terms"] = "Year"
write.csv(FinalBCoef, "C:/Users/Conducta/Dropbox/PHD/Git/Sibling_Insurance/CoefInsA")
```
# Plots

```{r}
plot(allEffects(BestInsA),type = "response")


ef <- effect("Sib_died", BestInsA)
x <- as.data.frame(ef)
summary(x)
ggplot(x, aes(Sib_died, fit, color=Sib_died)) + geom_point() +
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=0.4) +
  theme_bw(base_size=12)
```


# Diagnostics
```{r}
check_collinearity(BestInsA)
res = simulateResiduals(BestInsA)
plot(res)
testDispersion(res)
testUniformity(res)
testOutliers(res)
testQuantiles(res)
testZeroInflation(res)
```



