---
title: "Insurance_Cox_2"
author: "Ivan Bizberg"
date: "12/4/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)
```

# Prepare environement
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
library(lubridate)

library(performance)
library(DHARMa)
library(effects)
library(Greg)

library(lme4)
library(coxme)
library(survminer)
library(survival)
library(ordinal)
library(glmmTMB)

path = "Conducta"

source(str_glue("C:/Users/{path}/Dropbox/PHD/Custom functions/Censoring.R"))
```



# Import environemental conditions to survival data
```{r eval=FALSE}
# Add climwin windows for this data 

ClimData = read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/ClimateVariables4.0.csv"), sep = ",", 
                    header = T,stringsAsFactors = F) %>%
  rename(Date = time) %>% mutate(Date = ymd(Date)) %>% arrange(Date) %>% 
  mutate(SST = as.numeric(SST)) %>% 
  glimpse()

# Data impute missing climatic data 
Clim_imput = ClimData %>% arrange(Date) %>% select(Date , SST, Chl, Area_Rain) %>%
  recipe(~ .) %>% 
  step_rollimpute(all_of(c("SST", "Chl", "Area_Rain")), window = 15, statistic = mean) %>%
  prep() %>% bake(., new_data = NULL)

# Check imputation
colSums(is.na(Clim_imput))
```

# Import data    
```{r eval=TRUE}
Mother <- read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/RawData4.5.csv")) %>% 
  mutate(across(c(FECHFINAL1, FECHFINAL2, FECHFINAL3, ECLOSION1, ECLOSION2, ECLOSION3, ESTECLOS1, ESTECLOS2, ESTECLOS3, FECHHUEVO1, FECHHUEVO2, FECHHUEVO3, PUESTA1), ymd)) %>%
  rename(dmESTPUESTA1_ = dmESTPUESTA1) %>% 
  rename(Clutch = PUESTA, Brood = NIDADA) %>% 
  Censoring(., 60) %>% 
  mutate(FinalDate1 = ESTECLOS1 + Time601) %>% 
  mutate(FinalDate2 = ESTECLOS2 + Time602) %>% 
  mutate(FinalDate3 = ESTECLOS3 + Time603) 


# Remove nest established before arrival 
Mother_inc <- Mother %>% filter(!(!is.na(CONLLEGADA) & Arrival_date > ESTECLOS1)) # Remove nest where chicks hatched before nest monitoring because we don't know the brood size.
```

# Create new data for analysis BROODS OF 2
```{r eval=TRUE}
# Clean data
InsuranceData <-
  Mother_inc %>% 
  filter(!SEMANIPULO == "t") %>% 
  filter(Clutch == 2, Brood == 2) %>% 
  filter(!((!is.na(ECLOSION1) & !is.na(ECLOSION2)) & ECLOSION2 < ECLOSION1)) %>% # Remove chick B that hatched before chicks A (Probably an error at determining rank) (n = 195)
  filter(!((!is.na(ECLOSION1) & !is.na(FECHFINAL1)) & ECLOSION1 > FECHFINAL1)) %>% # Remove typo error (n = 2)
  filter(!((!is.na(ECLOSION2) & !is.na(FECHFINAL2)) & ECLOSION2 > FECHFINAL2)) %>%  # Remove typo error (n = 3)
  filter(!(Nest_OrderFemale > 1)) %>% # We could add male renest (n = -64)
  filter(!(FECHFINAL1 == FECHFINAL2 & Death601 == 1 & Death602 == 1)) %>% # We don't want chicks that died at the same date Sib_died==NA not 0
  mutate(Sib_died2 = case_when((Death601 == 1 & FECHFINAL1 < FinalDate2) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(Sib_died1 = case_when((Death602 == 1 & FECHFINAL2 < FinalDate1) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(SibFechFinal2 = FECHFINAL1) %>% 
  mutate(SibFechFinal1 = FECHFINAL2) 

# Edit data
InsuranceEdit <- InsuranceData %>% 
  rename(LastSibAge2 = LastAge1, LastSibAge1 = LastAge2) %>% 
  select(c(contains(c("Sib_died", "SibFechFinal")),
           ESTECLOS1, ESTECLOS2, 
           FinalDate1, FinalDate2,
           Time601, Time602,
           Death601, Death602,
           CoupleExpLocal,
           RealMotherAge, ANILLOHEMB, CONFIRMHEMB,
           RealFatherAge, ANILLOMACH, CONFIRMMACH,
           PROPORTIONALRANK, EstHatchAsynchro12_, NIDO, WORKYEAR)) %>% 
  mutate(across(contains(c("Sib_died", "Death60", "Time", "ESTECLOS", "FinalDate", "SibFechFinal")), as.character)) %>% 
  pivot_longer(all_of(ends_with(c("1", "2"))), names_to = c("col", "Status"), names_pattern = "(.*)(.)") %>%  
  pivot_wider(names_from = col) %>% # Split chick A and chick B
  mutate(Status = recode(Status, `1` = "ChickA", `2` = "ChickB")) %>% 
  mutate(across(c("Time60"), as.numeric)) %>% 
  drop_na(Death60)

# write.csv(InsuranceEdit, "InsuranceEdit_2.csv")  
```


## Create data for survival analisis counting form
```{r eval=FALSE}
DataCountingProcess = InsuranceEdit %>% 
  mutate(across(c(everything(), -Time60), as.character)) %>% # Step needed for greg package
  timeSplitter(by = 3, 
               event_var = "Death60",
               time_var = "Time60") %>% 
  mutate(Death = factor(Death60,
                        levels = 0:1,
                        labels = c("Alive", "Death"))) %>%
  mutate(across(c(Death60), as.character)) %>% 
  mutate(across(c(PROPORTIONALRANK, Death60), as.numeric)) %>% 
  mutate(across(c(ESTECLOS, FinalDate), ymd)) %>% 
  mutate(Date_Start_time = ESTECLOS + Start_time, Date_Stop_time = ESTECLOS + (Stop_time - 1)) %>% glimpse()

# Add climdata to counting data
ClimCount <- DataCountingProcess %>% 
  rowwise() %>% 
  mutate(listChl = list(ClimData$Chl[ClimData$Date %within% interval(Date_Start_time, Date_Stop_time)])) %>%
  mutate(listSST = list(ClimData$SST[ClimData$Date %within% interval(Date_Start_time, Date_Stop_time)])) %>% 
  mutate(listArea_rain = list(ClimData$Area_Rain[ClimData$Date %within% interval(Date_Start_time, Date_Stop_time)])) %>% 
      ungroup() %>% 
  mutate(
    Chl = map_dbl(listChl, mean, na.rm = T),
    SST = map_dbl(listSST, mean, na.rm = T),
    Area_rain = map_dbl(listArea_rain, mean, na.rm = T))

ClimDATACount <- ClimCount %>% select(-contains("list"))
write_csv(ClimDATACount, "DATAclimraw_ins_2.csv")
```


# Prepare data for analysis A 
```{r}
# mutate sib death into counting form
DATA <- read.csv("DATAclimraw_ins_2.csv") %>% # DATA_ins_2_rmChl.csv if we don't want chl, DATA_ins_2.csv
  mutate(across(c(Date_Start_time, Date_Stop_time, SibFechFinal), ymd)) %>% 
  mutate(Sib_died_count = case_when(((Sib_died == 1) & (Date_Start_time < SibFechFinal)) ~ 0,
                                    TRUE ~ as.numeric(Sib_died)), .after = "Sib_died") 
DATA %>% glimpse()

# Fix some remaining na that cause problems to cox model 
Nests <- read.csv("InsuranceEdit_2.csv") %>% filter(Status == "ChickA") %>% select(NIDO, Sib_died) %>% mutate(Sib_died = as.numeric(Sib_died))
CountNests <- DATA %>% filter(Status == "ChickA") %>% 
  drop_na(SST) %>% 
  # drop_na(Chl) %>% # remove if analysis without chl
  select(NIDO, Sib_died_count) %>% 
  group_by(NIDO) %>% 
  summarise(Sib_diedmax = max(Sib_died_count, na.rm = T))

Nest_rm_sibdeath <- left_join(Nests, CountNests, by = "NIDO") %>% filter(Sib_diedmax != Sib_died) %>% .$NIDO 
Nest_rm_death <- DATA %>% filter(Status == "ChickA") %>% filter(Death60 == 1 & is.na(SST)) %>% .$NIDO 

DATA_naomit <- DATA %>% filter(!NIDO %in% Nest_rm_sibdeath) %>% 
  filter(!NIDO %in% Nest_rm_death) %>% 
  glimpse()


SampleSize <- DATA_naomit %>% count(NIDO, Sib_died, Death60) %>% count(Death60, Sib_died); SampleSize
write_csv(SampleSize, "SampleSize_2.csv")

# write_csv(DATA_naomit, "DATA_ins_2_naomit.csv")
# write_csv(DATA_naomit, "DATA_ins_2_naomit_rmChl.csv")

```

# Select model covariates
```{r}
# Final data
DATA_Cox <- read.csv("DATA_ins_2_naomit_rmChl.csv") # DATA_ins_2_naomit_rmChl.csv

Insurance_Analysis <- DATA_Cox %>% 
  filter(Status == "ChickA") %>% 
  mutate(across(c(CoupleExpLocal, RealMotherAge, RealFatherAge, EstHatchAsynchro12_), as.numeric)) %>%
  mutate(across(c(WORKYEAR, Sib_died, Sib_died_count), as.character)) %>% 
  mutate(across(c(where(is.numeric), -Death60, -Start_time, -Stop_time), arm::rescale)) %>% 
  select(Start_time, Stop_time, Death60, Sib_died_count, PROPORTIONALRANK, SST, Area_rain,
         EstHatchAsynchro12_,
         # RealMotherAge, ANILLOHEMB, CONFIRMHEMB,
         # RealFatherAge, ANILLOMACH, CONFIRMMACH,
         # CoupleExpLocal,
         # Chl
         NIDO, WORKYEAR, Status) %>% 
  # filter(CONFIRMHEMB == "t", !ANILLOHEMB == "SA") %>%
  # filter(CONFIRMMACH == "t", !ANILLOMACH == "SA") %>%
  drop_na() %>% 
  glimpse()

SampleSize <- Insurance_Analysis %>% count(NIDO, Sib_died, Death60) %>% count(Death60, Sib_died); SampleSize
n_Brood_2A <- Insurance_Analysis %>% count(NIDO) %>% count()%>% pull
n_Brood_2A_rmPArents <- Insurance_Analysis %>% count(NIDO) %>% count()%>% pull
```
## CoxModel 
```{r eval=TRUE}
# Insurance_Analysis %<>% mutate(Sib_died = fct_relevel(Sib_died, "0", after = 3L))
levels(Insurance_Analysis$Sib_died)

Cox <- coxme(Surv(Start_time, Stop_time, Death60) ~ Sib_died_count +
               PROPORTIONALRANK + EstHatchAsynchro12_ +
               Sib_died_count : PROPORTIONALRANK +
               Sib_died_count : SST + # No Sign
               SST + 
               I(SST^2) +
               Area_rain +
               I(Area_rain^2) +
               # RealFatherAge +
               # I(RealFatherAge^2) +
               # CoupleExpLocal +
               (1|WORKYEAR) + (1|NIDO),
             data = Insurance_Analysis)

summary(Cox)


saveRDS(Cox, file = "FinalIns_Cox_A2_rmChl.rds")
```
## Cox Diagnostic

# Run Cox Diagnostic
```{r eval=FALSE}

Cox <- coxph(Surv(Start_time, Stop_time, Death60) ~ Sib_died +
               PROPORTIONALRANK +
               # Sib_died : Chl + # No Sign
               # Sib_died : SST + 
               Chl +
               I(Chl^2) +
               SST + 
               I(SST^2) +
               Area_rain +
               I(Area_rain^2) +
               # RealMotherAge +
               # I(RealMotherAge^2) +
               # CoupleExpLocal +
               (1|WORKYEAR) + (1|NIDO),
             data = Insurance_Analysis)

# check_collinearity(Coxme)
rms::vif(Coxph)

zph <- cox.zph(Coxph) ; zph
ggcoxzph(zph)

aa_fit <-aareg(Surv(Start_time, Stop_time, Death601) ~ SibPresence +
               PROPORTIONALRANK +
               # SibPresence : Chl + # No Sign
               SibPresence : SST +
               Chl +
               I(Chl^2) +
               SST + 
               I(SST^2) +
               Area_rain +
               I(Area_rain^2) + 
               # RealMotherAge +
               # I(RealMotherAge^2) +
               # CoupleExpLocal +
               frailty(NIDO),
             data = ClimCount_naomit)

# autoplot(aa_fit)


# Final Checking influential observations

# type = "dfbeta" , type = "deviance"


ggcoxdiagnostics(Cox, type = "dfbeta",
                 linear.predictions = FALSE, ggtheme = theme_bw()) # Looks good 

ggcoxdiagnostics(Cox, type = "deviance",
                 linear.predictions = FALSE, ggtheme = theme_bw()) # We see more negative values correspond to individual that "lived too long". Only problem with diagnostic

# Identify outliers
library(coxrobust)
res_mart = resid(Cox,type="martingale") %>% stack()# martingale or deviance
res_mart %>% #dplyr::slice_max(values, n = 100) %>%
  ggplot(aes(ind, values)) + geom_point()

# Final Checking non linearity

ggcoxfunctional(Surv(Start_time, Stop_time, Death601) ~ SibPresence +
               PROPORTIONALRANK +
               # SibPresence : Chl + # No Sign
               # SibPresence : SST +
               Chl +
               I(Chl^2) +
               SST + 
               I(SST^2) +
               Area_rain +
               I(Area_rain^2) + 
               # RealMotherAge +
               # I(RealMotherAge^2) +
               # CoupleExpLocal +
               frailty(NIDO),
             data = ClimCount_naomit)
  
  
  
```

# Prepare data for analysis B
```{r}
# mutate sib death into counting form
DATA <- read.csv("DATA_ins_2_naomit_rmChl.csv") %>% # DATA_ins_2_rmChl.csv if we don't want chl, DATA_ins_2.csv
  mutate(across(c(Date_Start_time, Date_Stop_time, SibFechFinal), ymd)) %>% 
  mutate(Sib_died_count = case_when(((Sib_died == 1) & (Date_Start_time < SibFechFinal)) ~ 0,
                                    TRUE ~ as.numeric(Sib_died)), .after = "Sib_died") 
DATA %>% glimpse()

# Fix some remaining na that cause problems to cox model 
Nests <- read.csv("InsuranceEdit_2.csv") %>% filter(Status == "ChickB") %>% select(NIDO, Sib_died) %>% mutate(Sib_died = as.numeric(Sib_died))
CountNests <- DATA %>% filter(Status == "ChickB") %>% 
  drop_na(SST) %>% 
  # drop_na(Chl) %>% # comment out if analysis without chl
  select(NIDO, Sib_died_count) %>% 
  group_by(NIDO) %>% 
  summarise(Sib_diedmax = max(Sib_died_count, na.rm = T))

Nest_rm_sibdeath <- left_join(Nests, CountNests, by = "NIDO") %>% filter(Sib_diedmax != Sib_died) %>% .$NIDO 
Nest_rm_death <- DATA %>% filter(Status == "ChickB") %>% filter(Death60 == 1 & is.na(SST)) %>% .$NIDO 

DATA_naomit <- DATA %>% filter(!NIDO %in% Nest_rm_sibdeath) %>% 
  filter(!NIDO %in% Nest_rm_death) %>% 
  glimpse()


SampleSize <- DATA_naomit %>% count(NIDO, Sib_died, Death60) %>% count(Death60, Sib_died); SampleSize
# write_csv(DATA_naomit, "DATA_ins_2_naomit_rmChl_B.csv")
```

# Select model covariates B
```{r}
# Final data
DATA_Cox <- read.csv("DATA_ins_2_naomit_rmChl_B.csv") # DATA_ins_2_naomit_rmChl.csv


Insurance_Analysis <- DATA_Cox %>% 
  filter(Status == "ChickB") %>% 
  mutate(across(c(CoupleExpLocal, RealMotherAge, RealFatherAge, EstHatchAsynchro12_), as.numeric)) %>%
  mutate(across(c(WORKYEAR, Sib_died, Sib_died_count), as.character)) %>% 
  mutate(across(c(where(is.numeric), -Death60, -Start_time, -Stop_time), arm::rescale)) %>% 
  select(Start_time, Stop_time, Death60, Sib_died_count, Sib_died, PROPORTIONALRANK, SST, Area_rain,
         EstHatchAsynchro12_,
         # RealMotherAge, ANILLOHEMB, CONFIRMHEMB,
         # RealFatherAge, ANILLOMACH, CONFIRMMACH,
         # CoupleExpLocal,
         # Chl
         NIDO, WORKYEAR, Status) %>% 
  # filter(CONFIRMHEMB == "t", !ANILLOHEMB == "SA") %>%
  # filter(CONFIRMMACH == "t", !ANILLOMACH == "SA") %>%
  drop_na() %>% 
  glimpse()


SampleSize <- DATA %>% count(NIDO, Sib_died, Death60) %>% count(Death60, Sib_died); SampleSize
n_Brood_2B <- Insurance_Analysis %>% count(NIDO) %>% count()%>% pull
n_Brood_2B_rmPArents <- Insurance_Analysis %>% count(NIDO) %>% count()%>% pull
```

## CoxModel 
```{r eval=FALSE}
Insurance_Analysis %<>% mutate(Sib_died = fct_relevel(Sib_died_count1, "0", after = 3L))
levels(Insurance_Analysis$Sib_died)

Coxa <- coxme(Surv(Start_time, Stop_time, Death60) ~ Sib_died_count +
               PROPORTIONALRANK + EstHatchAsynchro12_ +
               # Sib_died_count : PROPORTIONALRANK + # No Sign
               Sib_died_count : SST +
               SST + 
               I(SST^2) +
               Area_rain +
               I(Area_rain^2) +
               # RealFatherAge +
               # I(RealFatherAge^2) +
               # CoupleExpLocal +
               (1|WORKYEAR) + (1|NIDO),
             data = Insurance_Analysis)

summary(Coxa)

saveRDS(Coxa, file = "FinalIns_Cox_B2_rmChl.rds")
```

SST has a stronger negatiove effect in chick B survival when chick A didn't died


# Sample size 
```{r}
Sample_size <- data.frame(
  Sample_size = c("A2", "A2_rmParents", "B2", "B2_rmPArents"),
  n = c(n_Brood_2A, n_Brood_2A_rmPArents, n_Brood_2B, n_Brood_2B_rmPArents)
  )
write.csv(Sample_size, "SampleSize_2.csv")
```
































# Other
```{r eval=FALSE}
summary(CoxA)
summary(CoxB)


CoxA<- readRDS("Insurance_Cox_A2_naParents.rds") # remove parents SST:SIB
CoxA<- readRDS("Insurance_Cox_A2_naParents_Chlint.rds") # remove parents Chl:SIB
CoxA<- readRDS("Insurance_Cox_A2_naParents_F.rds") # ]Chl:SIB females age
CoxA<- readRDS("Insurance_Cox_B2_naParents_rm.rds") # remove parent no interaction
CoxA<- readRDS("Insurance_Cox_A2_rmChl_Final.rds") # remove Chl 
CoxA<- readRDS("Insurance_Cox_A2_rmChlParents.rds") # remove Chl and parents 
CoxA<- readRDS("Insurance_Cox_A2.rds"); summary(CoxB)
CoxB<- readRDS("Insurance_Cox_B2_naParents.rds"); summary(CoxB)
CoxB<- readRDS("Insurance_Cox_B2_naParents_Chlint.rds"); summary(CoxB)
CoxB<- readRDS("Insurance_Cox_B2_naParents_F.rds"); summary(CoxB)
CoxB<- readRDS("Insurance_Cox_B2_naParents_rm.rds"); summary(CoxB)
CoxB<- readRDS("Insurance_Cox_B2.rds"); summary(CoxB)
CoxB<- readRDS("Insurance_Cox_B2_Final.rds"); summary(CoxB)
CoxB<- readRDS("Insurance_Cox_B2_rmChlParents.rds"); summary(CoxB) #Model 2


```
