---
title: "Insurance_Cox3"
author: "Ivan Bizberg"
date: "12/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Prepare environement
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
library(lubridate)

library(performance)
library(DHARMa)
library(effects)
library(Greg)

library(lme4)
library(coxme)
library(survminer)
library(survival)
library(ordinal)
library(glmmTMB)

path = "Conducta"

source(str_glue("C:/Users/{path}/Dropbox/PHD/Custom functions/Censoring.R"))
```



# Import environemental conditions to survival data
```{r eval=FALSE}
# Add climwin windows for this data 

ClimData = read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/ClimateVariables4.0.csv"), sep = ",", 
                    header = T,stringsAsFactors = F) %>%
  rename(Date = time) %>% mutate(Date = ymd(Date)) %>% arrange(Date) %>% 
  mutate(SST = as.numeric(SST)) %>% 
  glimpse()

# Data impute missing climatic data 
Clim_imput = ClimData %>% arrange(Date) %>% select(Date , SST, Chl, Area_Rain) %>%
  recipe(~ .) %>% 
  step_rollimpute(all_of(c("SST", "Chl", "Area_Rain")), window = 15, statistic = mean) %>%
  prep() %>% bake(., new_data = NULL)

# Check imputation
colSums(is.na(Clim_imput))
```

# Import data    
```{r eval=FALSE}
Mother <- read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/RawData4.5.csv")) %>% 
  mutate(across(c(FECHFINAL1, FECHFINAL2, FECHFINAL3, ECLOSION1, ECLOSION2, ECLOSION3, ESTECLOS1, ESTECLOS2, ESTECLOS3, FECHHUEVO1, FECHHUEVO2, FECHHUEVO3, PUESTA1), ymd)) %>%
  rename(dmESTPUESTA1_ = dmESTPUESTA1) %>% 
  rename(Clutch = PUESTA, Brood = NIDADA) %>% 
  Censoring(., 60) %>% 
  mutate(FinalDate1 = ESTECLOS1 + Time601) %>% 
  mutate(FinalDate2 = ESTECLOS2 + Time602) %>% 
  mutate(FinalDate3 = ESTECLOS3 + Time603) %>% 
  mutate(SibFechFinalB1 = FECHFINAL2) %>% 
  mutate(SibFechFinalC1 = FECHFINAL3) %>% 
  mutate(SibFechFinalA2 = FECHFINAL1) %>% 
  mutate(SibFechFinalC2 = FECHFINAL3) %>% 
  mutate(SibFechFinalA3 = FECHFINAL1) %>%  
  mutate(SibFechFinalB3 = FECHFINAL2) 

# Remove nest established before arrival 
Mother_inc <- Mother %>% filter(!(!is.na(CONLLEGADA) & Arrival_date > ESTECLOS1)) # Remove nest where chicks hatched before nest monitoring because we don't know the brood size.
```

# Create new data for analysis BROODS OF 3 
```{r eval=FALSE}
# Mutate data
InsuranceData3 <-
  Mother %>% #names() %>% sort() 
  filter(SEMANIPULO == "f") %>% 
  filter(Clutch == 3, Brood == 3) %>% 
  filter(DESTHUEVO3 == "e") %>% # Confirm there is no typo error 
  filter(!(Nest_OrderFemale > 1)) %>% # We could add male renest (n = -n)
  mutate(Sib_died1 = case_when((Death602 == 1 & FECHFINAL2 < FinalDate1) | (Death603 == 1 & FECHFINAL3 < FinalDate1) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(BSib_died1= case_when((Death602 == 1 & FECHFINAL2 < FinalDate1) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(CSib_died1 = case_when((Death603 == 1 & FECHFINAL3 < FinalDate1) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(ASib_died2 = case_when((Death601 == 1 & FECHFINAL1 < FinalDate2) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(CSib_died2 = case_when((Death603 == 1 & FECHFINAL3 < FinalDate2) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(Sib_died3 = case_when((Death601 == 1 & FECHFINAL1 < FinalDate3) | (Death602 == 1 & FECHFINAL2 < FinalDate3) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(ASib_died3 = case_when((Death601 == 1 & FECHFINAL1 < FinalDate3) ~ 1, 
                               TRUE ~ 0)) %>% 
  mutate(BSib_died3 = case_when((Death602 == 1 & FECHFINAL2 < FinalDate3) ~ 1, 
                               TRUE ~ 0)) 

# Clean data
Insurance_C <- InsuranceData3 %>% filter(!((FECHFINAL3 == FECHFINAL2 & Death603 == 1 & Death602 == 1) | (FECHFINAL3 == FECHFINAL1 & Death603 == 1 & Death601 == 1))) %>% 
  filter(!((!is.na(ECLOSION1) & !is.na(ECLOSION3)) & ECLOSION3 < ECLOSION1)) %>% # Remove chick C that hatched before chicks A (safer to remove them) 
  filter(!((!is.na(ECLOSION2) & !is.na(ECLOSION3)) & ECLOSION3 < ECLOSION2)) %>% # Remove chick C that hatched before chicks B (Probably an error at determining rank) 
  filter(!((!is.na(ECLOSION3) & !is.na(FECHFINAL3)) & ECLOSION3 > FECHFINAL3)) # Remove typo error 

Insurance_B <- InsuranceData3 %>% filter(!((FECHFINAL1 == FECHFINAL2 & Death601 == 1 & Death602 == 1) | (FECHFINAL2 == FECHFINAL3 & Death602 == 1 & Death603 == 1))) %>% 
  filter(!((!is.na(ECLOSION1) & !is.na(ECLOSION2)) & ECLOSION2 < ECLOSION1)) %>% 
  filter(!((!is.na(ECLOSION3) & !is.na(ECLOSION2)) & ECLOSION3 < ECLOSION2)) %>%
  filter(!((!is.na(ECLOSION2) & !is.na(FECHFINAL2)) & ECLOSION2 > FECHFINAL2))

Insurance_A <- InsuranceData3 %>% filter(!((FECHFINAL1 == FECHFINAL1 & Death601 == 1 & Death602 == 1) | (FECHFINAL1 == FECHFINAL3 & Death601 == 1 & Death603 == 1))) %>% 
  filter(!((!is.na(ECLOSION1) & !is.na(ECLOSION2)) & ECLOSION2 < ECLOSION1)) %>% 
  filter(!((!is.na(ECLOSION3) & !is.na(ECLOSION1)) & ECLOSION3 < ECLOSION1)) %>% 
  filter(!((!is.na(ECLOSION1) & !is.na(FECHFINAL1)) & ECLOSION1 > FECHFINAL1))

# Edit to long data for chick A B and C
Broods_3 <- list(Insurance_A, Insurance_B, Insurance_C)

for (i in 1:3) {
  
  Data_frame <- Broods_3[[i]] %>% 
    select(c(contains(c("Sib_died", "Death60", "Time60", "EstHatchAsynchro", "SibFechFinal", "FinalDate")), 
             ESTECLOS1, ESTECLOS2, ESTECLOS3,
             ANILLOHEMB, RealMotherAge, CONFIRMHEMB, 
             ANILLOMACH, RealFatherAge, CONFIRMMACH, 
             CoupleExpLocal,
             PROPORTIONALRANK, NIDO, WORKYEAR)) %>% 
    mutate(across(c(contains(c("Sib_died", "Death60", "Time", "FinalDate", "SibFechFinal")), 
                             ESTECLOS1, ESTECLOS2, ESTECLOS3), as.character)) %>% 
    pivot_longer(all_of(ends_with(c("1", "2", "3"))), names_to = c("col", "Status"), names_pattern = "(.*)(.)") %>%  
    pivot_wider(names_from = col) %>% # Split chick A, chick B, C
    mutate(Status = recode(Status, `1` = "ChickA", `2` = "ChickB", `3` = "ChickC")) %>% 
    mutate(across(c("Time60"), as.numeric)) %>% 
    drop_na(Death60)
  
  write.csv(Data_frame, str_glue("EditInsurance_{i}.csv"))
  
  DataCountingProcess = Data_frame %>% 
    mutate(across(c(everything(), -Time60), as.character)) %>% # Step needed for greg package
    timeSplitter(by = 3, 
                 event_var = "Death60",
                 time_var = "Time60") %>% 
    mutate(Death = factor(Death60,
                          levels = 0:1,
                          labels = c("Alive", "Death"))) %>% 
    mutate(across(c(Death60), as.character)) %>% 
    mutate(across(c(PROPORTIONALRANK, Death60), as.numeric)) %>% 
    mutate(across(c(ESTECLOS, FinalDate), ymd)) %>% 
    mutate(Date_Start_time = ESTECLOS + Start_time, Date_Stop_time = ESTECLOS + (Stop_time - 1)) %>% glimpse()
  
  # Add climdata to counting data
  ClimCount <- DataCountingProcess %>% 
    rowwise() %>% 
    mutate(listChl = list(ClimData$Chl[ClimData$Date %within% interval(Date_Start_time, Date_Stop_time)])) %>%
    mutate(listSST = list(ClimData$SST[ClimData$Date %within% interval(Date_Start_time, Date_Stop_time)])) %>% 
    mutate(listArea_rain = list(ClimData$Area_Rain[ClimData$Date %within% interval(Date_Start_time, Date_Stop_time)])) %>% 
    ungroup() %>% 
    mutate(
      Chl = map_dbl(listChl, mean, na.rm = T),
      SST = map_dbl(listSST, mean, na.rm = T),
      Area_rain = map_dbl(listArea_rain, mean, na.rm = T)) 
  
  # Sample size & data (save)

  SampleSize <- ClimCount %>% count(NIDO, Sib_died, Death60) %>% count(Death60, Sib_died); SampleSize
  write_csv(SampleSize, str_glue("SampleSize_3{i}.csv"))
  
  ClimCount <- ClimCount %>% select(-contains("list"))
  write_csv(ClimCount, str_glue("DATAclimraw_ins_3{i}.csv"))
}
```

# Import created data and preprocess it
```{r message=FALSE}
DATA_A <- read.csv("DATAclimraw_ins_31.csv") %>% 
  filter(Status == "ChickA") %>% 
  select(-SibFechFinalA, -ASib_died) %>% 
  rowwise() %>% 
  mutate(SibFechFinal = min(SibFechFinalB, SibFechFinalC)) %>% 
  ungroup() %>% 
  mutate(Sib_died_count = case_when(((Sib_died == 1) & (Date_Start_time < SibFechFinal)) ~ 0,
                                    TRUE ~ as.numeric(Sib_died)), .after = "Sib_died")

# Fix some remaining na that cause problems to cox model 
Nests <- read.csv("EditInsurance_1.csv") %>% filter(Status == "ChickA") %>% select(NIDO, Sib_died) %>% mutate(Sib_died = as.numeric(Sib_died))
CountNests <- DATA_A %>% filter(Status == "ChickA") %>% 
  drop_na(SST) %>% 
  # drop_na(Chl) %>% # remove if analysis without chl
  select(NIDO, Sib_died_count) %>% 
  group_by(NIDO) %>% 
  summarise(Sib_diedmax = max(Sib_died_count, na.rm = T))

Nest_rm_sibdeath <- left_join(Nests, CountNests, by = "NIDO") %>% filter(Sib_diedmax != Sib_died) %>% .$NIDO 
Nest_rm_death <- DATA_A %>% filter(Status == "ChickA") %>% filter(Death60 == 1 & is.na(SST)) %>% .$NIDO 

DATA_naomit <- DATA_A %>% filter(!NIDO %in% Nest_rm_sibdeath) %>% 
  filter(!NIDO %in% Nest_rm_death) %>%
  glimpse()


SampleSize <- DATA_naomit %>% count(NIDO, Sib_died, Death60) %>% count(Death60, Sib_died); SampleSize
write_csv(SampleSize, "SampleSize_3A.csv")

# write_csv(DATA_naomit, "DATA_ins_3A_naomit.csv")
# write_csv(DATA_naomit, "DATA_ins_3A_naomit_rmChl.csv")


# Data C
DATA_C <- read.csv("DATAclimraw_ins_33.csv") %>% 
  filter(Status == "ChickC") %>% 
  select(-SibFechFinalC, -CSib_died) %>% 
  rowwise() %>% 
  mutate(SibFechFinal = min(SibFechFinalB, SibFechFinalA)) %>% 
  ungroup() %>% 
  mutate(Sib_died_count = case_when(((Sib_died == 1) & (Date_Start_time < SibFechFinal)) ~ 0,
                                    TRUE ~ as.numeric(Sib_died)), .after = "Sib_died")


# Fix some remaining na that cause problems to cox model 
Nests <- read.csv("EditInsurance_3.csv") %>% filter(Status == "ChickC") %>% select(NIDO, Sib_died) %>% mutate(Sib_died = as.numeric(Sib_died))
CountNests <- DATA_C %>% filter(Status == "ChickC") %>% 
  drop_na(SST) %>% 
  # drop_na(Chl) %>% # remove if analysis without chl
  select(NIDO, Sib_died_count) %>% 
  group_by(NIDO) %>% 
  summarise(Sib_diedmax = max(Sib_died_count, na.rm = T))

Nest_rm_sibdeath <- left_join(Nests, CountNests, by = "NIDO") %>% filter(Sib_diedmax != Sib_died) %>% .$NIDO 
Nest_rm_death <- DATA_C %>% filter(Status == "ChickC") %>% filter(Death60 == 1 & is.na(SST)) %>% .$NIDO 

DATA_naomit <- DATA_C %>% filter(!NIDO %in% Nest_rm_sibdeath) %>% 
  filter(!NIDO %in% Nest_rm_death) %>%
  glimpse()



SampleSize <- DATA_naomit %>% count(NIDO, Sib_died, Death60) %>% count(Death60, Sib_died); SampleSize
write_csv(SampleSize, "SampleSize_3C.csv")

# write_csv(DATA_naomit, "DATA_ins_3C_naomit.csv")
# write_csv(DATA_naomit, "DATA_ins_3C_naomit_rmChl.csv")

```
# Data B
DATA_B <- read_csv("DATAclimraw_ins_32.csv") %>%
  filter(Status == "ChickB") %>% 
  select(-SibFechFinalB, -BSib_died) %>% 
  mutate(ASib_died = if_else(Date_Start_time < SibFechFinalA, "0", "1")) %>% 
  mutate(CSib_died = if_else(Date_Start_time < SibFechFinalC, "0", "1")) 



# Select model covariates Cox A
```{r}
DATA_3A <- read.csv("DATA_ins_3A_naomit_rmChl.csv")
Insurance_Analysis <- DATA_3A %>%
  mutate(across(c(CoupleExpLocal, RealMotherAge, RealFatherAge, EstHatchAsynchro12_), as.numeric)) %>% 
  mutate(across(c(WORKYEAR, Sib_died), as.character)) %>% 
  mutate(across(c(where(is.numeric), -Death60, -Sib_died_count, -Start_time, -Stop_time), arm::rescale)) %>% 
  select(Start_time, Stop_time, Death60, Sib_died_count, Sib_died, PROPORTIONALRANK, SST, Area_rain,
         EstHatchAsynchro13_,
         # RealMotherAge, ANILLOHEMB, CONFIRMHEMB,
         RealFatherAge, ANILLOMACH, CONFIRMMACH,
         # CoupleExpLocal,
         # Chl
         NIDO, WORKYEAR
  ) %>% 
  # filter(CONFIRMHEMB == "t", !ANILLOHEMB == "SA") %>%
  filter(CONFIRMMACH == "t", !ANILLOMACH == "SA") %>%
  drop_na() %>%
  glimpse()

SampleSize <- Insurance_Analysis %>% count(NIDO, Sib_died, Death60) %>% count(Death60, Sib_died); SampleSize
n_Brood_3A <- Insurance_Analysis %>% count(NIDO) %>% count() %>% pull
n_Brood_3A_rmPArents <- Insurance_Analysis %>% count(NIDO) %>% count() %>% pull
## CoxModel C
# Insurance_Analysis %<>% mutate(Sib_died = fct_relevel(Sib_died, "0", after = 3L))
levels(Insurance_Analysis$Sib_died)

CoxA <- coxme(Surv(Start_time, Stop_time, Death60) ~ Sib_died_count +
               PROPORTIONALRANK + EstHatchAsynchro13_ + 
               # Sib_died_count : PROPORTIONALRANK + # Sign
               # Sib_died_count : SST + # No Sign
               SST + 
               I(SST^2) +
               Area_rain +
               I(Area_rain^2) +
               RealFatherAge +
               I(RealFatherAge^2) +
               # CoupleExpLocal +
               (1|WORKYEAR) + (1|NIDO),
             data = Insurance_Analysis)

summary(CoxA)
saveRDS(CoxA, file = "FinalIns_Cox_A3_Father_rmChl.rds")
```



# Select model covariates Cox C
```{r}
DATA_3C <- read.csv("DATA_ins_3C_naomit_rmChl.csv")
Insurance_Analysis <- DATA_3C  %>%
  mutate(across(c(CoupleExpLocal, RealMotherAge, RealFatherAge, EstHatchAsynchro12_), as.numeric)) %>% 
  mutate(across(c(WORKYEAR, Sib_died), as.character)) %>% 
  mutate(across(c(where(is.numeric), -Death60, -Sib_died_count, -Start_time, -Stop_time), arm::rescale)) %>% 
  select(Start_time, Stop_time, Death60, Sib_died_count, PROPORTIONALRANK, SST, Area_rain,
         EstHatchAsynchro13_,
         RealMotherAge, ANILLOHEMB, CONFIRMHEMB,
         # RealFatherAge, ANILLOMACH, CONFIRMMACH,
         # CoupleExpLocal,
         # Chl
         NIDO, WORKYEAR
  ) %>% 
  filter(CONFIRMHEMB == "t", !ANILLOHEMB == "SA") %>%
  # filter(CONFIRMMACH == "t", !ANILLOMACH == "SA") %>%
  drop_na() %>%
  glimpse()

SampleSize <- Insurance_Analysis %>% count(NIDO, Sib_died, Death60) %>% count(Death60, Sib_died); SampleSize
n_Brood_3C <- Insurance_Analysis %>% count(NIDO) %>% count() %>% pull
n_Brood_3C_rmPArents <- Insurance_Analysis %>% count(NIDO) %>% count()%>% pull

## CoxModel C

# Insurance_Analysis %<>% mutate(Sib_died = fct_relevel(Sib_died, "0", after = 3L))
levels(Insurance_Analysis$Sib_died)

CoxC <- coxme(Surv(Start_time, Stop_time, Death60) ~ Sib_died_count +
               PROPORTIONALRANK + EstHatchAsynchro13_ +
               # Sib_died_count : PROPORTIONALRANK + # No Sign
               # Sib_died_count : SST + # No Sign
               SST + 
               I(SST^2) +
               Area_rain +
               I(Area_rain^2) +
               RealMotherAge +
               I(RealMotherAge^2) +
               # CoupleExpLocal +
               (1|WORKYEAR) + (1|NIDO),
             data = Insurance_Analysis)

summary(CoxC)
saveRDS(CoxC, file = "Final_Cox_C3_Mother_rmChl.rds")
```


# Models Results FINAL
```{r}
Cox_A3 <- readRDS("Final_Cox_A3_rmChlParents.rds") %>% jstable:::coxmeTable() %>% mutate(`exp(beta)` = exp(beta), .after = "beta") %>%
  cbind(confint(readRDS("Final_Cox_A3_rmChlParents.rds")))

Cox_A3F <- readRDS("Final_Cox_A3_Father_rmChl.rds") %>% jstable:::coxmeTable() %>% mutate(`exp(beta)` = exp(beta), .after = "beta") %>%
  cbind(confint(readRDS("Final_Cox_A3_Father_rmChl.rds")))

Cox_A3M <- readRDS("Final_Cox_A3_Mother_rmChl.rds") %>% jstable:::coxmeTable() %>% mutate(`exp(beta)` = exp(beta), .after = "beta") %>%
  cbind(confint(readRDS("Final_Cox_A3_Mother_rmChl.rds")))

Cox_C3 <- readRDS("Final_Cox_C3_rmChlParents.rds") %>% jstable:::coxmeTable() %>% mutate(`exp(beta)` = exp(beta), .after = "beta") %>%
  cbind(confint(readRDS("Final_Cox_C3_rmChlParents.rds")))

Cox_C3F <- readRDS("Final_Cox_C3_Father_rmChl.rds") %>% jstable:::coxmeTable() %>% mutate(`exp(beta)` = exp(beta), .after = "beta") %>%
  cbind(confint(readRDS("Final_Cox_C3_Father_rmChl.rds")))

Cox_C3M <- readRDS("Final_Cox_C3_Mother_rmChl.rds") %>% jstable:::coxmeTable() %>% mutate(`exp(beta)` = exp(beta), .after = "beta") %>%
  cbind(confint(readRDS("Final_Cox_C3_Mother_rmChl.rds")))


```


# Run Cox Diagnostic
```{r eval=FALSE}

Coxph <- coxph(Surv(Start_time, Stop_time, Death60) ~ Sib_died +
               PROPORTIONALRANK +
               # Sib_died : Chl + # No Sign
               # Sib_died : SST + 
               Chl +
               I(Chl^2) +
               SST + 
               I(SST^2) +
               Area_rain +
               I(Area_rain^2) +
               # RealMotherAge +
               # I(RealMotherAge^2) +
               # CoupleExpLocal +
               frailty(NIDO),
             data = Insurance_Analysis)

# check_collinearity(Coxme)
rms::vif(Cox_C3)

zph <- cox.zph(Coxph) ; zph
ggcoxzph(zph)

aa_fit <-aareg(Surv(Start_time, Stop_time, Death60) ~ Sib_died +
               PROPORTIONALRANK +
               # Sib_died : Chl + # No Sign
               # Sib_died : SST + 
               Chl +
               I(Chl^2) +
               SST + 
               I(SST^2) +
               Area_rain +
               I(Area_rain^2) +
               # RealMotherAge +
               # I(RealMotherAge^2) +
               # CoupleExpLocal +
               frailty(NIDO),
             data = Insurance_Analysis)

plot(aa_fit)


# Final Checking influential observations

ggcoxdiagnostics(Coxph, type = "dfbeta",
                 linear.predictions = FALSE, ggtheme = theme_bw()) # Looks good 

ggcoxdiagnostics(Coxph, type = "deviance",
                 linear.predictions = FALSE, ggtheme = theme_bw()) # We see more negative values correspond to individual that "lived too long". slight concern with diagnostic

# Identify outliers
library(coxrobust)
res_mart = resid(Coxph,type="martingale") %>% stack()# martingale or deviance
res_mart %>% #dplyr::slice_max(values, n = 100) %>%
  ggplot(aes(ind, values)) + geom_point()

# Final Checking non linearity

ggcoxfunctional(Surv(Start_time, Stop_time, Death60) ~ Sib_died +
               PROPORTIONALRANK +
               # Sib_died : Chl + # No Sign
               # Sib_died : SST + 
               Chl +
               I(Chl^2) +
               SST + 
               I(SST^2) +
               Area_rain +
               I(Area_rain^2) +
               # RealMotherAge +
               # I(RealMotherAge^2) +
               # CoupleExpLocal +
               frailty(NIDO),
             data = Insurance_Analysis)
  
```





# Results 
```{r}
readRDS("Insurance_Cox_C3_rmChlParents.rds")
```


# Sample size 
```{r}
Sample_size <- data.frame(
  Sample_size = c("A3", "A3_rmParents", "C3", "C3_rmPArents"),
  n = c(n_Brood_3A, n_Brood_3A_rmPArents, n_Brood_3C, n_Brood_3C_rmPArents)
  )
write.csv(Sample_size, "SampleSize_3.csv")
```
















# Prepare data for analysis B
```{r eval=FALSE}
Insurance_Analysis <- DATA_B %>%
  mutate(across(c(CoupleExpLocal, RealMotherAge, RealFatherAge, EstHatchAsynchro12_), as.numeric)) %>% 
  mutate(across(c(WORKYEAR, Sib_died), as.character)) %>% 
  mutate(across(c(where(is.numeric), -Death60, -Start_time, -Stop_time), arm::rescale)) %>% 
  select(
    -CoupleExpLocal,
    -RealMotherAge, -ANILLOHEMB, -CONFIRMHEMB,
    -RealFatherAge, -ANILLOMACH, -CONFIRMMACH
  ) %>% 
  # filter(CONFIRMHEMB == TRUE, !ANILLOHEMB == "SA") %>%
  # filter(CONFIRMMACH == TRUE, !ANILLOMACH == "SA") %>% 
  glimpse()

SampleSize <- Insurance_Analysis %>% count(NIDO, Sib_died, Death60) %>% count(Death60, Sib_died); SampleSize

## CoxModel B

# Insurance_Analysis %<>% mutate(Sib_died = fct_relevel(Sib_died, "0", after = 3L))
levels(Insurance_Analysis$Sib_died)

Cox <- coxme(Surv(Start_time, Stop_time, Death60) ~ ASib_died +
               PROPORTIONALRANK +
               # Sib_died : Chl + # No Sign
               # Sib_died : SST + 
               Chl +
               I(Chl^2) +
               SST + 
               I(SST^2) +
               Area_rain +
               I(Area_rain^2) +
               # RealMotherAge +
               # I(RealMotherAge^2) +
               # CoupleExpLocal +
               (1|WORKYEAR) + (1|NIDO),
             data = Insurance_Analysis)

summary(Cox)
saveRDS(Cox, file = "Insurance_Cox_B3.rds")
```
This analysis can't be run because to small sample size to analyse both the effect of chick a death and chick c death
